---
title: "Compiled and prepare data "
author: "Juliana E Trach"
date: "`r Sys.Date()`"
output: pdf_document
toc: yes
toc_depth: 2
fontsize: 12pt
---
\newpage

# Abstract
This script takes the raw data for each subject, concatenates it, adds columns for analysis purposes, and performs exclusions. Each chunk of code can take >5min to run so pre-compiled data is also provided (in compiledData) that will work with the main anaysis scripts.

#  Prep data for Experiment 1
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
# set up workspace
rm(list=ls(all=TRUE))
setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment1"
# load libraries
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(Rmisc)

# read in files
file_paths = fs::dir_ls(datadir)
compiledData = data.frame()
for (i in seq_along(file_paths)){
  newSubjData = read_csv(file = file_paths[[i]], col_types = cols(hierarchy = col_character(),question_order = col_character()))
  compiledData = rbind(compiledData, newSubjData)
}


# clean up data
compiledData$rt = as.numeric(compiledData$rt)
compiledData$time_elapsed = as.numeric(compiledData$time_elapsed)
compiledData$key_press = as.numeric(compiledData$key_press)
compiledData$stim = as.numeric(compiledData$stim)
compiledData$corrresp = as.numeric(compiledData$corrresp)



# sort data into prac and test
compiledData = filter(compiledData, trialType %in% c('rl','motor','motorRepeat','postmotor'))
pracData = filter(compiledData, phase == "prac")
testData_ExperimentOne = filter(compiledData, phase %in% c("motor","test","postmotor"))

# get some variables
prolificNums = unique(testData_ExperimentOne$subject)
subjNums_all = unique(testData_ExperimentOne$subject)
N_all = length(prolificNums)

allResps_new = c(65,83,68,70,72,74,75,76)
LH_new = c(65,83,68,70)
RH_new = c(72,74,75,76)
coupletOne_new = c(65,83,72,74)
coupletTwo_new = c(68,70,75,76)

allResps = c(1,2,3,4,5,6,7,8)

#make a column for recoded responses to make life easier
testData_ExperimentOne$corrrespAll = NA
testData_ExperimentOne$finger_press = NA
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 65] = 1
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 83] = 2
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 68] = 3
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 70] = 4
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 72] = 5
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 74] = 6
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 75] = 7
testData_ExperimentOne$corrrespAll[testData_ExperimentOne$corrresp == 76] = 8

testData_ExperimentOne$finger_press[ testData_ExperimentOne$key_press == 65] = 1
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 83] = 2
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 68] = 3
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 70] = 4
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 72] = 5
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 74] = 6
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 75] = 7
testData_ExperimentOne$finger_press[testData_ExperimentOne$key_press == 76] = 8

ns = length(allResps)

# add more info to trials before saving
testData_ExperimentOne$iter = NA
testData_ExperimentOne$zscoredRTs = NA
testData_ExperimentOne$logRTs = NA
testData_ExperimentOne$hand = NA
testData_ExperimentOne$couplet = NA
testData_ExperimentOne$handSwitch = NA
testData_ExperimentOne$coupletSwitch = NA
testData_ExperimentOne$fingerSwitch = NA
testData_ExperimentOne$handSwitch_actual = NA
testData_ExperimentOne$coupletSwitch_actual = NA
testData_ExperimentOne$fingerSwitch_actual = NA
testData_ExperimentOne$respHand = NA
testData_ExperimentOne$respCouplet = NA
testData_ExperimentOne$corrHand = NA
testData_ExperimentOne$corrCouplet = NA

for(ai in 1:N_all){
  testData_ExperimentOne$zscoredRTs[testData_ExperimentOne$subject == subjNums_all[ai]] = scale(testData_ExperimentOne$rt[testData_ExperimentOne$subject == subjNums_all[ai]])
  testData_ExperimentOne$logRTs[testData_ExperimentOne$subject == subjNums_all[ai]] = log(testData_ExperimentOne$rt[testData_ExperimentOne$subject == subjNums_all[ai]])
  # add iteration numbers
  for(bi in 1:ns){
    idx = which(testData_ExperimentOne$subject == subjNums_all[ai]&testData_ExperimentOne$corrrespAll == allResps[bi] & testData_ExperimentOne$phase == 'test')
    for (ci in 1:length(idx)){
      testData_ExperimentOne$stimNum[idx[ci]] = bi
      testData_ExperimentOne$iter[idx[ci]] = ci
    }
  }
  trialNum_idx = which(testData_ExperimentOne$subject == subjNums_all[ai] & testData_ExperimentOne$trialType == 'rl')
  testData_ExperimentOne$trialNum[trialNum_idx] = c(1:length(which(testData_ExperimentOne$subject == subjNums_all[ai] & testData_ExperimentOne$trialType == 'rl')))
}
for (xi in 1:dim(testData_ExperimentOne)[1]){
  # put in correct hand and couplet
  if(testData_ExperimentOne$corrresp[xi] %in% RH_new){
    testData_ExperimentOne$hand[xi] = 'R'
  }else if (testData_ExperimentOne$corrresp[xi] %in% LH_new){
    testData_ExperimentOne$hand[xi] = 'L'
  }
  
  if(testData_ExperimentOne$corrresp[xi] %in% coupletOne_new){
    testData_ExperimentOne$couplet[xi] = 1
  }else if (testData_ExperimentOne$corrresp[xi] %in% coupletTwo_new){
    testData_ExperimentOne$couplet[xi] = 2
  }
  
  # put in the hand and couplet of the response
  if(testData_ExperimentOne$key_press[xi] %in% RH_new){
    testData_ExperimentOne$respHand[xi] = 'R'
  }else if (testData_ExperimentOne$key_press[xi] %in% LH_new){
    testData_ExperimentOne$respHand[xi] = 'L'
  }
  
  if(testData_ExperimentOne$key_press[xi] %in% coupletOne_new){
    testData_ExperimentOne$respCouplet[xi] = 1
  }else if (testData_ExperimentOne$key_press[xi] %in% coupletTwo_new){
    testData_ExperimentOne$respCouplet[xi] = 2
  }
  
  # 1 for correct hand, 0 for incorrect
  if(is.na(testData_ExperimentOne$respHand[xi])){
    testData_ExperimentOne$corrHand[xi] = 0
  } else if(testData_ExperimentOne$hand[xi] == testData_ExperimentOne$respHand[xi]){
    testData_ExperimentOne$corrHand[xi] = 1
  }else if (testData_ExperimentOne$hand[xi] != testData_ExperimentOne$respHand[xi]){
    testData_ExperimentOne$corrHand[xi] = 0
  }
  if(is.na(testData_ExperimentOne$respCouplet[xi])){
    testData_ExperimentOne$corrCouplet[xi] = 0
  }else if(testData_ExperimentOne$couplet[xi] == testData_ExperimentOne$respCouplet[xi]){
    testData_ExperimentOne$corrCouplet[xi] = 1
  }else if (testData_ExperimentOne$couplet[xi] != testData_ExperimentOne$respCouplet[xi]){
    testData_ExperimentOne$corrCouplet[xi] = 0
  }
  
}

for(di in 1:(dim(testData_ExperimentOne)[1]-1)){
  #hand switches
  if(testData_ExperimentOne$hand[di] == testData_ExperimentOne$hand[di+1]){
    testData_ExperimentOne$handSwitch[di+1]= 0
  } else if(testData_ExperimentOne$hand[di] != testData_ExperimentOne$hand[di+1]){
    testData_ExperimentOne$handSwitch[di+1] = 1
  }
  if(testData_ExperimentOne$couplet[di] == testData_ExperimentOne$couplet[di+1]){
    testData_ExperimentOne$coupletSwitch[di+1]= 0
  } else if(testData_ExperimentOne$couplet[di] != testData_ExperimentOne$couplet[di+1]){
    testData_ExperimentOne$coupletSwitch[di+1] = 1
  }
  #switches and repeats for finger
  if(testData_ExperimentOne$corrresp[di] == testData_ExperimentOne$corrresp[di+1]){
    testData_ExperimentOne$fingerSwitch[di+1] = 0
  }else{
    testData_ExperimentOne$fingerSwitch[di+1] = 1
  }
  
  # same but with actual responses
  if(is.na(testData_ExperimentOne$respHand[di]) | is.na(testData_ExperimentOne$respHand[di+1])){
    testData_ExperimentOne$handSwitch_actual[di]= NA
    testData_ExperimentOne$handSwitch_actual[di+1]=NA
  }else if(testData_ExperimentOne$respHand[di] == testData_ExperimentOne$respHand[di+1]){
    testData_ExperimentOne$handSwitch_actual[di+1]= 0
  } else if(testData_ExperimentOne$respHand[di] != testData_ExperimentOne$respHand[di+1]){
    testData_ExperimentOne$handSwitch_actual[di+1] = 1
  }
  if(is.na(testData_ExperimentOne$respCouplet[di]) | is.na(testData_ExperimentOne$respCouplet[di+1]) ){
    testData_ExperimentOne$coupletSwitch_actual[di]= NA
    testData_ExperimentOne$coupletSwitch_actual[di+1]= NA
  }else if(testData_ExperimentOne$respCouplet[di] == testData_ExperimentOne$respCouplet[di+1]){
    testData_ExperimentOne$coupletSwitch_actual[di+1]= 0
  } else if(testData_ExperimentOne$respCouplet[di] != testData_ExperimentOne$respCouplet[di+1]){
    testData_ExperimentOne$coupletSwitch_actual[di+1] = 1
  }
  #switches and repeats for finger
  if(is.na(testData_ExperimentOne$key_press[di])| is.na(testData_ExperimentOne$key_press[di+1])){
    testData_ExperimentOne$fingerSwitch_actual[di+1]= NA
    testData_ExperimentOne$fingerSwitch_actual[di]= NA
  }else if(testData_ExperimentOne$key_press[di] == testData_ExperimentOne$key_press[di+1]){
    testData_ExperimentOne$fingerSwitch_actual[di+1] = 0
  }else{
    testData_ExperimentOne$fingerSwitch_actual[di+1] = 1
  }
  
  if(is.na(testData_ExperimentOne$trialNum[di])){
    testData_ExperimentOne$handSwitch[di] = testData_ExperimentOne$handSwitch[di-1]
    testData_ExperimentOne$coupletSwitch[di] = testData_ExperimentOne$coupletSwitch[di-1]
    testData_ExperimentOne$fingerSwitch[di] = testData_ExperimentOne$fingerSwitch[di-1]
    testData_ExperimentOne$handSwitch_actual[di] = testData_ExperimentOne$handSwitch_actual[di-1]
    testData_ExperimentOne$coupletSwitch_actual[di] = testData_ExperimentOne$coupletSwitch_actual[di-1]
    testData_ExperimentOne$fingerSwitch_actual[di] = testData_ExperimentOne$fingerSwitch_actual[di-1]
  }else if(testData_ExperimentOne$trialNum[di] == 1){
    testData_ExperimentOne$handSwitch[di] = NA
    testData_ExperimentOne$coupletSwitch[di] = NA
    testData_ExperimentOne$fingerSwitch[di] = NA
    testData_ExperimentOne$handSwitch_actual[di] = NA
    testData_ExperimentOne$coupletSwitch_actual[di] = NA
    testData_ExperimentOne$fingerSwitch_actual[di] = NA
  }
}
testData_ExperimentOne$combinedType = NA
testData_ExperimentOne$combinedType[testData_ExperimentOne$coupletSwitch_actual == 0&testData_ExperimentOne$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentOne$combinedType[testData_ExperimentOne$coupletSwitch_actual == 0&testData_ExperimentOne$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentOne$combinedType[testData_ExperimentOne$coupletSwitch_actual == 1&testData_ExperimentOne$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentOne$combinedType[testData_ExperimentOne$coupletSwitch_actual == 1&testData_ExperimentOne$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentOne$combinedType[testData_ExperimentOne$fingerSwitch_actual == 0] = 'rep/rep/rep'
testData_ExperimentOne$combinedType[testData_ExperimentOne$trialNum == 1] = NA

testData_ExperimentOne$treeDistance = NA
testData_ExperimentOne$treeDistance[testData_ExperimentOne$coupletSwitch_actual == 0&testData_ExperimentOne$handSwitch_actual == 0] = 2
testData_ExperimentOne$treeDistance[testData_ExperimentOne$coupletSwitch_actual == 0&testData_ExperimentOne$handSwitch_actual == 1] = 6
testData_ExperimentOne$treeDistance[testData_ExperimentOne$coupletSwitch_actual == 1&testData_ExperimentOne$handSwitch_actual == 0] =4
testData_ExperimentOne$treeDistance[testData_ExperimentOne$coupletSwitch_actual == 1&testData_ExperimentOne$handSwitch_actual == 1] = 6
testData_ExperimentOne$treeDistance[testData_ExperimentOne$fingerSwitch_actual == 0] = 0
testData_ExperimentOne$treeDistance[testData_ExperimentOne$trialNum == 1] = NA

# Fix issue with motorRepeat in postmotor phase classified in wrong phase
repeatIdx = which(testData_ExperimentOne$trialType == 'motorRepeat')

for(ei in repeatIdx){
  if(testData_ExperimentOne$phase[ei-1] == 'postmotor'){
    testData_ExperimentOne$phase[ei] = 'postmotor'
  }
}

ExperimentOne = testData_ExperimentOne %>% filter(trialType == 'rl', iter < 128)

#### EXCLUSIONS ####
accuracyExclusions = ExperimentOne %>% group_by(subject, stimNum) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
includeSub_strict = NA

for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) == 8){
    includeSub_strict[ai] = 1
  }else{
    includeSub_strict[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
subjNums_included_strict = subjNums_all[includeSub_strict ==1]
#now filter for just these subjects that aren't excluded 
ExperimentOne_withExclusions = ExperimentOne %>% filter(subject %in% subjNums_all[includeSub ==1])
testData_ExperimentOne_withExclusions = testData_ExperimentOne %>% filter(subject %in% subjNums_all[includeSub ==1])
#Add a column for the strict exclusion criterion to see if that helps
ExperimentOne_withExclusions$includeStrict = NA
ExperimentOne_withExclusions$includeStrict[ExperimentOne_withExclusions$subject %in% c(subjNums_included_strict)] = 1

# Add finger distance column 
ExperimentOne_withExclusions$fingerDistance[1] = NA
ExperimentOne_withExclusions$fingerDistance[2:length(ExperimentOne_withExclusions$fingerDistance)] = abs(ExperimentOne_withExclusions$finger_press[2:length(ExperimentOne_withExclusions$fingerDistance)]-ExperimentOne_withExclusions$finger_press[1:length(ExperimentOne_withExclusions$finger_press)-1])
ExperimentOne_withExclusions$fingerDistance[ExperimentOne_withExclusions$trialNum == 1] = NA
# Add previous corr response column 
ExperimentOne_withExclusions$corrrespAll_prev[1] = NA
ExperimentOne_withExclusions$corrrespAll_prev[2:length(ExperimentOne_withExclusions$corrresp)] = ExperimentOne_withExclusions$corrrespAll[1:length(ExperimentOne_withExclusions$corrresp)-1]
ExperimentOne_withExclusions$corrrespAll_prev[ExperimentOne_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
ExperimentOne_withExclusions$finger_press_prev[1] = NA
ExperimentOne_withExclusions$finger_press_prev[2:length(ExperimentOne_withExclusions$finger_press)] = ExperimentOne_withExclusions$finger_press[1:length(ExperimentOne_withExclusions$corrresp)-1]
ExperimentOne_withExclusions$finger_press_prev[ExperimentOne_withExclusions$trialNum == 1] = NA

#add feature sw column
featureSwitchArray = array(c(0,1,1,2,1,2,2,3,1,0,2,1,2,1,3,2,1,2,0,1,2,3,1,2,2,1,1,0,3,2,2,1,1,2,2,3,0,1,1,2,2,1,3,2,1,0,2,1,2,3,1,2,1,2,0,1,3,2,2,1,2,1,1,0),dim = c(8,8))
# add path distances
treeDistanceArray = array(c(0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0,6,6,6,6,6,6,6,6,0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0),dim = c(8,8))

ExperimentOne_withExclusions$nFeatureSwitch[1] = NA
for(ai in 1:length(ExperimentOne_withExclusions$nFeatureSwitch)){
  prev = ExperimentOne_withExclusions$corrrespAll_prev[ai]
  curr = ExperimentOne_withExclusions$corrrespAll[ai]
  ExperimentOne_withExclusions$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
ExperimentOne_withExclusions$nFeatureSwitch[ExperimentOne_withExclusions$trialNum == 1] = NA

## add switch/rep for each level of hierarchy
ExperimentOne_withExclusions$topType = NA
ExperimentOne_withExclusions$midType = NA
ExperimentOne_withExclusions$lowType = NA
#top level
ExperimentOne_withExclusions$topType[ExperimentOne_withExclusions$handSwitch ==1] = 1
ExperimentOne_withExclusions$topType[ExperimentOne_withExclusions$handSwitch ==0] = 0
#mid level
ExperimentOne_withExclusions$midType[ExperimentOne_withExclusions$coupletSwitch ==1] = 1
ExperimentOne_withExclusions$midType[ExperimentOne_withExclusions$coupletSwitch ==0] = 0
#low level
for(bi in 2:length(ExperimentOne_withExclusions$lowType)){
  prev = ExperimentOne_withExclusions$corrrespAll_prev[bi]
  curr = ExperimentOne_withExclusions$corrrespAll[bi]
  if(ExperimentOne_withExclusions$trialNum[bi] == 1){
    ExperimentOne_withExclusions$lowType[bi] = NA 
  }else if(((prev %% 2 == 0) & (curr %%2 == 0)) | ((prev %% 2 != 0) & (curr %% 2 != 0))){
    ExperimentOne_withExclusions$lowType[bi] = 0
  }else{
    ExperimentOne_withExclusions$lowType[bi] = 1
  }
}
ExperimentOne_withExclusions = ExperimentOne_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

#### PREP MOTOR DATA FOR CORRECTION #### 
motorData_withExclusions_allRT = testData_ExperimentOne %>% filter(phase == 'motor', trialType == 'motor', corr == 1) 
motorData_withExclusions = motorData_withExclusions_allRT %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

#pull out second motor phase
postmotorData_withExclusions_allRT = testData_ExperimentOne_withExclusions %>% filter(phase == 'postmotor', trialType == 'postmotor', corr == 1) 
postmotorData_withExclusions = postmotorData_withExclusions_allRT %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum >3)

allmotorData_withExclusions = testData_ExperimentOne_withExclusions %>% filter(phase %in% c('motor','postmotor'), corr == 1, trialType %in% c('motor','postmotor')) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)
upperBound = mean(allmotorData_withExclusions$rt,na.rm = TRUE)+3*sd(allmotorData_withExclusions$rt,na.rm = TRUE)

allmotorData_withExclusions = allmotorData_withExclusions %>% filter(rt < upperBound)

motorStats = allmotorData_withExclusions %>% group_by(subject) %>% dplyr::summarise(avg = mean(rt,na.rm = TRUE),maxi = max(rt,na.rm = TRUE),mini = min(rt,na.rm =TRUE), trip = avg+3*sd(rt,na.rm = TRUE),tooFast = sum(rt < 150), tooSlow = sum(rt>900))

# do this in a hacky way rn to exclude super slow RTs
allmotorData_withExclusions$rtStrict = NA
allmotorData_withExclusions$rtStrict[allmotorData_withExclusions$rt < 900] = 1

allmotorData_withExclusions_corr = allmotorData_withExclusions %>% filter(trialType %in% c('motor','postmotor'), corr == 1, !is.na(fingerSwitch))
allmotorData_withExclusions_corr$rt_corr = allmotorData_withExclusions_corr$rt
allmotorData_withExclusions_corr$rtz_corr = allmotorData_withExclusions_corr$rtz

allmotorData_withExclusions_corr$rt_corr[allmotorData_withExclusions_corr$trialType == 'motorRepeat'] = NA
allmotorData_withExclusions_corr$rtz_corr[allmotorData_withExclusions_corr$trialType == 'motorRepeat'] = NA

#filter for correct responses
heatmapData_allmotorData_withExclusions_corr = data.frame(currResp = allmotorData_withExclusions_corr$key_press[2:length(allmotorData_withExclusions_corr$key_press)], prevResp = allmotorData_withExclusions_corr$key_press[1:length(allmotorData_withExclusions_corr$key_press)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum >3, !is.na(currResp), !is.na(prevResp)) %>% group_by(currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medRT = median(rt,na.rm =TRUE))

heatmapData_allmotorData_withExclusions_corr$prevResp = factor(heatmapData_allmotorData_withExclusions_corr$prevResp, levels = c(76,75,74,72,70,68,83,65))
heatmapData_allmotorData_withExclusions_corr$currResp = factor(heatmapData_allmotorData_withExclusions_corr$currResp, levels = c(65,83,68,70,72,74,75,76))

heatmapData_allTrials_resp_m_both = data.frame(subject = allmotorData_withExclusions_corr$subject[2:length(allmotorData_withExclusions_corr$subject)],currResp = allmotorData_withExclusions_corr$key_press[2:length(allmotorData_withExclusions_corr$key_press)], prevResp = allmotorData_withExclusions_corr$key_press[1:length(allmotorData_withExclusions_corr$key_press)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(76,75,74,72,70,68,83,65))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(65,83,68,70,72,74,75,76))

###### MOTOR CORRECTION ######
nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA
motorTransitions$rt = NA
motorTransitions$rt_both = NA
motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]
  
  motorTransitions$rt[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  
  
}

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]
    motorTransitions$rt[missingIdx[i]] = motorTransitions$rt[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT[missingIdx[i]] = motorTransitions$medRT[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    
    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_both[missingIdx[i]] = motorTransitions$medRT_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    
    motorTransitions$rt_strict[missingIdx[i]] = motorTransitions$rt_strict[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_strict[missingIdx[i]] = motorTransitions$medRT_strict[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    
    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentOne_withExclusions$rt_corrected = NA
ExperimentOne_withExclusions$medRT_corrected = NA

ExperimentOne_withExclusions$rt_corrected_both = NA
ExperimentOne_withExclusions$medRT_corrected_both = NA

ExperimentOne_withExclusions$rt_strict_corrected = NA
ExperimentOne_withExclusions$medRT_strict_corrected = NA

for(i in 1:length(ExperimentOne_withExclusions$rt_corrected)){
  if(ExperimentOne_withExclusions$trialNum[i] ==1){
    ExperimentOne_withExclusions$rt_corrected[i] = NA
  }else{
    prev = ExperimentOne_withExclusions$corrrespAll_prev[i]
    curr = ExperimentOne_withExclusions$finger_press[i]
    motorRT = motorTransitions$rt[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]
    
    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]
    
    ExperimentOne_withExclusions$rt_corrected[i] = ExperimentOne_withExclusions$rt[i] - motorRT
    
    ExperimentOne_withExclusions$rt_corrected_both[i] = ExperimentOne_withExclusions$rt[i] - motorRT_both
    
    
  }
}


##### STREAK PERFORMANCE ##### add a column to track consecutively correct trials
ExperimentOne_withExclusions$streak = NA
ExperimentOne_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentOne_withExclusions$corr)){
  trial = ExperimentOne_withExclusions$trialNum[ai]
  if(ExperimentOne_withExclusions$trialNum[ai-1]==(trial-1)){
    if(ExperimentOne_withExclusions$corr[ai]==1 & ExperimentOne_withExclusions$corr[ai-1]==1){
      ExperimentOne_withExclusions$streak[ai] = 1
    }else{
      ExperimentOne_withExclusions$streak[ai] = 0
    }
  }else{
    ExperimentOne_withExclusions$streak[ai] = 0
  }
}

for(ai in 2:length(ExperimentOne_withExclusions$corr)){
  trial = ExperimentOne_withExclusions$trialNum[ai]
  if(ExperimentOne_withExclusions$trialNum[ai-1]==(trial-1)){
    if(ExperimentOne_withExclusions$streak[ai]==1 & ExperimentOne_withExclusions$streak[ai-1]==1){
      ExperimentOne_withExclusions$longStreak[ai] = 1
    }else{
      ExperimentOne_withExclusions$longStreak[ai] = 0
    }
  }else{
    ExperimentOne_withExclusions$longStreak[ai] = 0
  }
}

ExperimentOne_withExclusions$streak[ExperimentOne_withExclusions$trialNum ==1] = NA

######### WRITE DATA TO FILE ########
write.csv(allmotorData_withExclusions, 'motorData_Experiment1_compiled.csv')
write.csv(ExperimentOne_withExclusions, 'Experiment1_compiled.csv')

```

# Prep data for EXPERIMENT 2
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
# set up workspace
# set up workspace
rm(list=ls(all=TRUE))

setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment2"
# load libraries
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(fabricatr)
library(Rmisc)
library(lme4)
library(rstatix)
library(MuMIn)

# read in data
  file_paths = fs::dir_ls(datadir)
  compiledData = data.frame()
  for (i in seq_along(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]], col_types = cols(hierarchy = col_character(),question_order = col_character()))
    compiledData = rbind(compiledData, newSubjData)
  }
  
  
  # clean up data
  compiledData$rt = as.numeric(compiledData$rt)
  compiledData$time_elapsed = as.numeric(compiledData$time_elapsed)
  compiledData$key_press = as.numeric(compiledData$key_press)
  compiledData$corrresp = as.numeric(compiledData$corrresp)
  
  
  
  # sort data into prac and test
  compiledData = filter(compiledData, trialType %in% c('rl','motor','motorRepeat'))
  pracData = filter(compiledData, phase == "prac")
  testData_ExperimentTwo = filter(compiledData, phase %in% c("motor","test"))
  
  # get some variables
  prolificNums = unique(testData_ExperimentTwo$subject)
  subjNums_all = unique(testData_ExperimentTwo$subject)
  N_all = length(prolificNums)
  
  allResps_new = c(65,83,68,70,72,74,75,76)
  LH_new = c(65,83,68,70)
  RH_new = c(72,74,75,76)
  
  # changed couplets to finger space
  coupletOne_new = c(68,70,72,74)
  coupletTwo_new = c(65,83,75,76)
  
  allResps = c(1,2,3,4,5,6,7,8)
  
  #make a column for recoded responses to make life easier
  
  testData_ExperimentTwo$corrrespAll = NA
  testData_ExperimentTwo$finger_press = NA
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 65] = 1
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 83] = 2
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 68] = 3
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 70] = 4
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 72] = 5
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 74] = 6
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 75] = 7
  testData_ExperimentTwo$corrrespAll[testData_ExperimentTwo$corrresp == 76] = 8
  
  testData_ExperimentTwo$finger_press[ testData_ExperimentTwo$key_press == 65] = 1
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 83] = 2
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 68] = 3
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 70] = 4
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 72] = 5
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 74] = 6
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 75] = 7
  testData_ExperimentTwo$finger_press[testData_ExperimentTwo$key_press == 76] = 8
  
  ns = length(allResps)
  # add more info to trials before saving
  testData_ExperimentTwo$iter = NA
  testData_ExperimentTwo$zscoredRTs = NA
  testData_ExperimentTwo$logRTs = NA
  testData_ExperimentTwo$hand = NA
  testData_ExperimentTwo$couplet = NA
  testData_ExperimentTwo$handSwitch = NA
  testData_ExperimentTwo$coupletSwitch = NA
  testData_ExperimentTwo$fingerSwitch = NA
  testData_ExperimentTwo$handSwitch_actual = NA
  testData_ExperimentTwo$coupletSwitch_actual = NA
  testData_ExperimentTwo$fingerSwitch_actual = NA
  testData_ExperimentTwo$respHand = NA
  testData_ExperimentTwo$respCouplet = NA
  testData_ExperimentTwo$corrHand = NA
  testData_ExperimentTwo$corrCouplet = NA
  for(ai in 1:N_all){
    testData_ExperimentTwo$zscoredRTs[testData_ExperimentTwo$subject == subjNums_all[ai]] = scale(testData_ExperimentTwo$rt[testData_ExperimentTwo$subject == subjNums_all[ai]])
    testData_ExperimentTwo$logRTs[testData_ExperimentTwo$subject == subjNums_all[ai]] = log(testData_ExperimentTwo$rt[testData_ExperimentTwo$subject == subjNums_all[ai]])
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(testData_ExperimentTwo$subject == subjNums_all[ai]&testData_ExperimentTwo$corrrespAll == allResps[bi] & testData_ExperimentTwo$phase == 'test')
      for (ci in 1:length(idx)){
        testData_ExperimentTwo$stimNum[idx[ci]] = bi
        testData_ExperimentTwo$iter[idx[ci]] = ci
      }
    }
    trialNum_idx = which(testData_ExperimentTwo$subject == subjNums_all[ai] & testData_ExperimentTwo$trialType == 'rl')
    testData_ExperimentTwo$trialNum[trialNum_idx] = c(1:length(which(testData_ExperimentTwo$subject == subjNums_all[ai] & testData_ExperimentTwo$trialType == 'rl')))
  }
  for (xi in 1:dim(testData_ExperimentTwo)[1]){
    # put in correct hand and couplet
    if(testData_ExperimentTwo$corrresp[xi] %in% RH_new){
      testData_ExperimentTwo$hand[xi] = 'R'
    }else if (testData_ExperimentTwo$corrresp[xi] %in% LH_new){
      testData_ExperimentTwo$hand[xi] = 'L'
    }
    
      if(testData_ExperimentTwo$corrresp[xi] %in% coupletOne_new){
      testData_ExperimentTwo$couplet[xi] = 1
    }else if (testData_ExperimentTwo$corrresp[xi] %in% coupletTwo_new){
      testData_ExperimentTwo$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(testData_ExperimentTwo$key_press[xi] %in% RH_new){
      testData_ExperimentTwo$respHand[xi] = 'R'
    }else if (testData_ExperimentTwo$key_press[xi] %in% LH_new){
      testData_ExperimentTwo$respHand[xi] = 'L'
    }
    
    if(testData_ExperimentTwo$key_press[xi] %in% coupletOne_new){
      testData_ExperimentTwo$respCouplet[xi] = 1
    }else if (testData_ExperimentTwo$key_press[xi] %in% coupletTwo_new){
      testData_ExperimentTwo$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(testData_ExperimentTwo$respHand[xi])){
      testData_ExperimentTwo$corrHand[xi] = 0
    } else if(testData_ExperimentTwo$hand[xi] == testData_ExperimentTwo$respHand[xi]){
      testData_ExperimentTwo$corrHand[xi] = 1
    }else if (testData_ExperimentTwo$hand[xi] != testData_ExperimentTwo$respHand[xi]){
      testData_ExperimentTwo$corrHand[xi] = 0
    }
     if(is.na(testData_ExperimentTwo$respCouplet[xi])){
      testData_ExperimentTwo$corrCouplet[xi] = 0
    }else if(testData_ExperimentTwo$couplet[xi] == testData_ExperimentTwo$respCouplet[xi]){
      testData_ExperimentTwo$corrCouplet[xi] = 1
    }else if (testData_ExperimentTwo$couplet[xi] != testData_ExperimentTwo$respCouplet[xi]){
      testData_ExperimentTwo$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(testData_ExperimentTwo)[1]-1)){
    #hand switches
    if(testData_ExperimentTwo$hand[di] == testData_ExperimentTwo$hand[di+1]){
      testData_ExperimentTwo$handSwitch[di+1]= 0
    } else if(testData_ExperimentTwo$hand[di] != testData_ExperimentTwo$hand[di+1]){
      testData_ExperimentTwo$handSwitch[di+1] = 1
    }
    if(testData_ExperimentTwo$couplet[di] == testData_ExperimentTwo$couplet[di+1]){
      testData_ExperimentTwo$coupletSwitch[di+1]= 0
    } else if(testData_ExperimentTwo$couplet[di] != testData_ExperimentTwo$couplet[di+1]){
      testData_ExperimentTwo$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(testData_ExperimentTwo$corrresp[di] == testData_ExperimentTwo$corrresp[di+1]){
      testData_ExperimentTwo$fingerSwitch[di+1] = 0
    }else{
      testData_ExperimentTwo$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(testData_ExperimentTwo$respHand[di]) | is.na(testData_ExperimentTwo$respHand[di+1])){
      if(is.na(testData_ExperimentTwo$respHand[di]) & is.na(testData_ExperimentTwo$respHand[di+1])){
        testData_ExperimentTwo$handSwitch_actual[di]= NA
        testData_ExperimentTwo$handSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$respHand[di])){
        testData_ExperimentTwo$handSwitch_actual[di]= NA
        testData_ExperimentTwo$handSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$respHand[di+1])){
        testData_ExperimentTwo$handSwitch_actual[di+1] = NA
      }

    }else if(testData_ExperimentTwo$respHand[di] == testData_ExperimentTwo$respHand[di+1]){
      testData_ExperimentTwo$handSwitch_actual[di+1]= 0
    } else if(testData_ExperimentTwo$respHand[di] != testData_ExperimentTwo$respHand[di+1]){
      testData_ExperimentTwo$handSwitch_actual[di+1] = 1
    }
    if(is.na(testData_ExperimentTwo$respCouplet[di]) | is.na(testData_ExperimentTwo$respCouplet[di+1])){
      if(is.na(testData_ExperimentTwo$respCouplet[di]) & is.na(testData_ExperimentTwo$respCouplet[di+1])){
        testData_ExperimentTwo$coupletSwitch_actual[di]= NA
        testData_ExperimentTwo$coupletSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$respCouplet[di])){
        testData_ExperimentTwo$coupletSwitch_actual[di]= NA
        testData_ExperimentTwo$coupletSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$respCouplet[di+1])){
        testData_ExperimentTwo$coupletSwitch_actual[di+1] = NA
      }
    }else if(testData_ExperimentTwo$respCouplet[di] == testData_ExperimentTwo$respCouplet[di+1]){
      testData_ExperimentTwo$coupletSwitch_actual[di+1]= 0
    } else if(testData_ExperimentTwo$respCouplet[di] != testData_ExperimentTwo$respCouplet[di+1]){
      testData_ExperimentTwo$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(testData_ExperimentTwo$key_press[di])| is.na(testData_ExperimentTwo$key_press[di+1])){
        if(is.na(testData_ExperimentTwo$key_press[di]) & is.na(testData_ExperimentTwo$key_press[di+1])){
        testData_ExperimentTwo$fingerSwitch_actual[di]= NA
        testData_ExperimentTwo$fingerSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$key_press[di])){
        testData_ExperimentTwo$fingerSwitch_actual[di]= NA
        testData_ExperimentTwo$fingerSwitch_actual[di+1]=NA
      }else if(is.na(testData_ExperimentTwo$key_press[di+1])){
        testData_ExperimentTwo$fingerSwitch_actual[di+1] = NA
      }
    }else if(testData_ExperimentTwo$key_press[di] == testData_ExperimentTwo$key_press[di+1]){
      testData_ExperimentTwo$fingerSwitch_actual[di+1] = 0
    }else{
      testData_ExperimentTwo$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(testData_ExperimentTwo$trialNum[di])){
      testData_ExperimentTwo$handSwitch[di] = testData_ExperimentTwo$handSwitch[di-1]
      testData_ExperimentTwo$coupletSwitch[di] = testData_ExperimentTwo$coupletSwitch[di-1]
      testData_ExperimentTwo$fingerSwitch[di] = testData_ExperimentTwo$fingerSwitch[di-1]
      testData_ExperimentTwo$handSwitch_actual[di] = testData_ExperimentTwo$handSwitch_actual[di-1]
      testData_ExperimentTwo$coupletSwitch_actual[di] = testData_ExperimentTwo$coupletSwitch_actual[di-1]
      testData_ExperimentTwo$fingerSwitch_actual[di] = testData_ExperimentTwo$fingerSwitch_actual[di-1]
    }else if(testData_ExperimentTwo$trialNum[di] == 1){
      testData_ExperimentTwo$handSwitch[di] = NA
      testData_ExperimentTwo$coupletSwitch[di] = NA
      testData_ExperimentTwo$fingerSwitch[di] = NA
      testData_ExperimentTwo$handSwitch_actual[di] = NA
      testData_ExperimentTwo$coupletSwitch_actual[di] = NA
      testData_ExperimentTwo$fingerSwitch_actual[di] = NA
    }
  }
  testData_ExperimentTwo$combinedType = NA
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$coupletSwitch_actual == 0&testData_ExperimentTwo$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$coupletSwitch_actual == 0&testData_ExperimentTwo$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$coupletSwitch_actual == 1&testData_ExperimentTwo$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$coupletSwitch_actual == 1&testData_ExperimentTwo$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$fingerSwitch_actual == 0] = 'rep/rep/rep'
testData_ExperimentTwo$combinedType[testData_ExperimentTwo$trialNum == 1] = NA

testData_ExperimentTwo$treeDistance = NA
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$coupletSwitch_actual == 0&testData_ExperimentTwo$handSwitch_actual == 0] = 2
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$coupletSwitch_actual == 0&testData_ExperimentTwo$handSwitch_actual == 1] = 6
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$coupletSwitch_actual == 1&testData_ExperimentTwo$handSwitch_actual == 0] =4
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$coupletSwitch_actual == 1&testData_ExperimentTwo$handSwitch_actual == 1] = 6
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$fingerSwitch_actual == 0] = 0
testData_ExperimentTwo$treeDistance[testData_ExperimentTwo$trialNum == 1] = NA

# exclude first trials
testData_ExperimentTwo = testData_ExperimentTwo %>% filter(trialNum > 3)
  # Fix issue with motorRepeat in postmotor phase classified in wrong phase
  repeatIdx = which(testData_ExperimentTwo$trialType == 'motorRepeat')
  

  for(ei in repeatIdx){
    if(testData_ExperimentTwo$phase[ei-1] == 'postmotor'){
      testData_ExperimentTwo$phase[ei] = 'postmotor'
    }
  }
  
ExperimentTwo = testData_ExperimentTwo %>% filter(trialType == 'rl', iter < 57)

#### EXCLUSIONS ####
accuracyExclusions = ExperimentTwo %>% group_by(subject, stimNum) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
includeSub_strict = NA

for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) == 8){
    includeSub_strict[ai] = 1
  }else{
    includeSub_strict[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
subjNums_included_strict = subjNums_all[includeSub_strict ==1]
#now filter for just these subjects that aren't excluded 
testData_ExperimentTwo_withExclusions = testData_ExperimentTwo %>% filter(subject %in% subjNums_all[includeSub ==1])

#Add a column for the strict exclusion criterion
testData_ExperimentTwo_withExclusions$includeStrict = NA
testData_ExperimentTwo_withExclusions$includeStrict[testData_ExperimentTwo_withExclusions$subject %in% c(subjNums_included_strict)] = 1

# Add finger distance column 
testData_ExperimentTwo_withExclusions$fingerDistance[1] = NA
testData_ExperimentTwo_withExclusions$fingerDistance[2:length(testData_ExperimentTwo_withExclusions$fingerDistance)] = abs(testData_ExperimentTwo_withExclusions$finger_press[2:length(testData_ExperimentTwo_withExclusions$fingerDistance)]-testData_ExperimentTwo_withExclusions$finger_press[1:length(testData_ExperimentTwo_withExclusions$finger_press)-1])
testData_ExperimentTwo_withExclusions$fingerDistance[testData_ExperimentTwo_withExclusions$trialNum == 1] = NA

# Add previous corr response column 
testData_ExperimentTwo_withExclusions$corrrespAll_prev[1] = NA
testData_ExperimentTwo_withExclusions$corrrespAll_prev[2:length(testData_ExperimentTwo_withExclusions$corrresp)] = testData_ExperimentTwo_withExclusions$corrrespAll[1:length(testData_ExperimentTwo_withExclusions$corrresp)-1]
testData_ExperimentTwo_withExclusions$corrrespAll_prev[testData_ExperimentTwo_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
testData_ExperimentTwo_withExclusions$finger_press_prev[1] = NA
testData_ExperimentTwo_withExclusions$finger_press_prev[2:length(testData_ExperimentTwo_withExclusions$finger_press)] = testData_ExperimentTwo_withExclusions$finger_press[1:length(testData_ExperimentTwo_withExclusions$corrresp)-1]
testData_ExperimentTwo_withExclusions$finger_press_prev[testData_ExperimentTwo_withExclusions$trialNum == 1] = NA



#add feature sw column
featureSwitchArray = array(c(0,1,1,2,3,2,2,1, 
                             1,0,2,1,2,3,1,2,
                             1,2,0,1,2,1,3,2,
                             2,1,1,0,1,2,2,3,
                             3,2,2,1,0,1,1,2,
                             2,3,1,2,1,0,2,1,
                             2,1,3,2,1,2,0,1,
                             1,2,2,3,2,1,1,0),dim = c(8,8))
testData_ExperimentTwo_withExclusions$nFeatureSwitch[1] = NA
testData_ExperimentTwo_withExclusions$nFeatureSwitch[is.na(testData_ExperimentTwo_withExclusions$treeDistance)] = NA

for(ai in 1:length(testData_ExperimentTwo_withExclusions$nFeatureSwitch)){
  prev = testData_ExperimentTwo_withExclusions$corrrespAll_prev[ai]
  curr = testData_ExperimentTwo_withExclusions$corrrespAll[ai]
  testData_ExperimentTwo_withExclusions$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
testData_ExperimentTwo_withExclusions$nFeatureSwitch[testData_ExperimentTwo_withExclusions$trialNum == 1] = NA

# add tree distance column 
treeDistanceArray = array(c(0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0,6,6,6,6,6,6,6,6,0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0),dim = c(8,8))


# MAKE SURE TO FILTER OUT EXTRA ITERATIONS and first 4 trials! (move earlier in code for future versions)
ExperimentTwo_withExclusions = testData_ExperimentTwo_withExclusions %>% filter(phase == 'test') %>% filter(iter < 57)
## add switch/rep for each level of hierarchy
ExperimentTwo_withExclusions$topType = NA
ExperimentTwo_withExclusions$midType = NA
ExperimentTwo_withExclusions$lowType = NA

#top level
ExperimentTwo_withExclusions$topType[ExperimentTwo_withExclusions$handSwitch ==1] = 1
ExperimentTwo_withExclusions$topType[ExperimentTwo_withExclusions$handSwitch ==0] = 0

#mid level
ExperimentTwo_withExclusions$midType[ExperimentTwo_withExclusions$coupletSwitch ==1] = 1
ExperimentTwo_withExclusions$midType[ExperimentTwo_withExclusions$coupletSwitch ==0] = 0


#low level
for(bi in 2:length(ExperimentTwo_withExclusions$lowType)){
  prev = ExperimentTwo_withExclusions$corrrespAll_prev[bi]
  curr = ExperimentTwo_withExclusions$corrrespAll[bi]
  if(ExperimentTwo_withExclusions$trialNum[bi] == 1){
   ExperimentTwo_withExclusions$lowType[bi] = NA 
  }else if(((prev %% 2 == 0) & (curr %% 2 == 0)) | ((prev %% 2 != 0) & (curr %% 2 != 0))){
    ExperimentTwo_withExclusions$lowType[bi] = 0
  }else{
    ExperimentTwo_withExclusions$lowType[bi] = 1
  }
}

ExperimentTwo_withExclusions = ExperimentTwo_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

allmotorData_withExclusions = testData_ExperimentTwo_withExclusions %>% filter(phase %in% c('motor'), corr == 1, trialType %in% c('motor'), subject %in% subjNums_included) %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)
motorUpperBound = mean(allmotorData_withExclusions$rt,na.rm = TRUE)+sd(allmotorData_withExclusions$rt,na.rm = TRUE)*3

allmotorData_withExclusions_corr = allmotorData_withExclusions %>% filter(trialType %in% c('motor'), corr == 1, !is.na(fingerSwitch))
allmotorData_withExclusions_corr$rt_corr = allmotorData_withExclusions_corr$rt
allmotorData_withExclusions_corr$rt_corr[allmotorData_withExclusions_corr$trialType == 'motorRepeat'] = NA

# heatmap array for BOTH motor tasks
heatmapData_allTrials_resp_m_both = data.frame(subject = allmotorData_withExclusions_corr$subject[2:length(allmotorData_withExclusions_corr$subject)],currResp = allmotorData_withExclusions_corr$key_press[2:length(allmotorData_withExclusions_corr$key_press)], prevResp = allmotorData_withExclusions_corr$key_press[1:length(allmotorData_withExclusions_corr$key_press)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(76,75,74,72,70,68,83,65))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(65,83,68,70,72,74,75,76))

# ok, so we want add a column onto the main RL dataframe we're working with that has the baseline corrected rts
# first let's make the motor dataframe easier to use by creating a dataframe with all of the possible combinations
nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA

motorTransitions$rt_both = NA
motorTransitions$medRT_both = NA

motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]

  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  motorTransitions$medRT_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$medianRT[mi]


  }

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]
    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_both[missingIdx[i]] = motorTransitions$medRT_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentTwo_withExclusions$rt_corrected_both = NA
ExperimentTwo_withExclusions$medRT_corrected_both = NA

ExperimentTwo_withExclusions$rt_strict_corrected = NA
ExperimentTwo_withExclusions$medRT_strict_corrected = NA

for(i in 1:length(ExperimentTwo_withExclusions$rt_corrected_both)){
  if(ExperimentTwo_withExclusions$trialNum[i] ==1){
    ExperimentTwo_withExclusions$rt_corrected[i] = NA
  }else{
    prev = ExperimentTwo_withExclusions$corrrespAll_prev[i]
    curr = ExperimentTwo_withExclusions$finger_press[i]

    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]
    motorRT_med_both = motorTransitions$medRT_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]

    
    ExperimentTwo_withExclusions$rt_corrected_both[i] = ExperimentTwo_withExclusions$rt[i] - motorRT_both
    ExperimentTwo_withExclusions$medRT_corrected_both[i] = ExperimentTwo_withExclusions$rt[i] - motorRT_med_both

  }
}
zscoredRT = ExperimentTwo_withExclusions %>% group_by(subject) %>% dplyr::summarise(rt_corrected_both_z = scale(rt))
ExperimentTwo_withExclusions$rt_corrected_both_z = zscoredRT$rt_corrected_both_z

#### STREAK TRIALS #####
ExperimentTwo_withExclusions$streak = NA
ExperimentTwo_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentTwo_withExclusions$corr)){
  trial = ExperimentTwo_withExclusions$trialNum[ai]
 if(ExperimentTwo_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentTwo_withExclusions$corr[ai]==1 & ExperimentTwo_withExclusions$corr[ai-1]==1){
   ExperimentTwo_withExclusions$streak[ai] = 1
   }else{
     ExperimentTwo_withExclusions$streak[ai] = 0
   }
 }else{
   ExperimentTwo_withExclusions$streak[ai] = 0
 }
}

for(ai in 2:length(ExperimentTwo_withExclusions$corr)){
  trial = ExperimentTwo_withExclusions$trialNum[ai]
 if(ExperimentTwo_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentTwo_withExclusions$streak[ai]==1 & ExperimentTwo_withExclusions$streak[ai-1]==1){
   ExperimentTwo_withExclusions$longStreak[ai] = 1
   }else{
     ExperimentTwo_withExclusions$longStreak[ai] = 0
   }
 }else{
   ExperimentTwo_withExclusions$longStreak[ai] = 0
 }
}

ExperimentTwo_withExclusions$streak[ExperimentTwo_withExclusions$trialNum ==1] = NA


######### WRITE DATA TO FILE ########
write.csv(allmotorData_withExclusions, 'motorData_Experiment2_compiled.csv')
write.csv(ExperimentTwo_withExclusions, 'Experiment2_compiled.csv')

```
# Prep data for EXPERIMENT 3
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
# set up workspace
rm(list=ls(all=TRUE))
setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment3"
# load libraries
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(fabricatr)
library(Rmisc)
library(lme4)
library(rstatix)
library(MuMIn)


# read in data
  file_paths = fs::dir_ls(datadir)
  compiledData = data.frame()
  for (i in seq_along(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]], col_types = cols(rt = col_double(),
  responses = col_character(),
  time_elapsed = col_double(),
  subject = col_character(),
  prolificID = col_character(),
  demoID = col_character(),
  trialType = col_character(),
  question_order = col_character(),
  key_press = col_character(),
  stim = col_character(),
  corrresp = col_double(),
  phase = col_character(),
  stimNum = col_double(),
  type = col_character(),
  trialNum = col_double(),
  corr = col_double(),
  repeatTrial = col_double(),
  motorSwitch = col_double(),
  pracCounter = col_double()))
    compiledData = rbind(compiledData, newSubjData)
  }
  
  
  # clean up data
  compiledData$rt = as.numeric(compiledData$rt)
  compiledData$time_elapsed = as.numeric(compiledData$time_elapsed)
  compiledData$key_press = as.numeric(compiledData$key_press)
  compiledData$stim = as.numeric(compiledData$stim)
  compiledData$corrresp = as.numeric(compiledData$corrresp)
  
  
  
  # sort data into prac and test
  compiledData = filter(compiledData, trialType %in% c('rl','motor','motorRepeat','postmotor'))
  pracData = filter(compiledData, phase == "prac")
  testData_ExperimentThree = filter(compiledData, phase %in% c("motor","test","postmotor"))
  
  # get some variables
  prolificNums = unique(testData_ExperimentThree$subject)
  subjNums_all = unique(testData_ExperimentThree$subject)
  N_all = length(prolificNums)
  
  allResps_new = c(65,83,68,70,72,74,75,76)
  LH_new = c(65,83,68,70)
  RH_new = c(72,74,75,76)
  coupletOne_new = c(65,83,72,74)
  coupletTwo_new = c(68,70,75,76)
  
  allResps = c(1,2,3,4,5,6,7,8)
  
  #make a column for recoded responses to make life easier
  
  testData_ExperimentThree$corrrespAll = NA
  testData_ExperimentThree$finger_press = NA
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 65] = 1
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 83] = 2
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 68] = 3
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 70] = 4
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 72] = 5
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 74] = 6
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 75] = 7
  testData_ExperimentThree$corrrespAll[testData_ExperimentThree$corrresp == 76] = 8
  
  testData_ExperimentThree$finger_press[ testData_ExperimentThree$key_press == 65] = 1
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 83] = 2
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 68] = 3
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 70] = 4
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 72] = 5
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 74] = 6
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 75] = 7
  testData_ExperimentThree$finger_press[testData_ExperimentThree$key_press == 76] = 8
  
  ns = length(allResps)
  # add more info to trials before saving
  testData_ExperimentThree$iter = NA
  testData_ExperimentThree$zscoredRTs = NA
  testData_ExperimentThree$logRTs = NA
  testData_ExperimentThree$hand = NA
  testData_ExperimentThree$couplet = NA
  testData_ExperimentThree$handSwitch = NA
  testData_ExperimentThree$coupletSwitch = NA
  testData_ExperimentThree$fingerSwitch = NA
  testData_ExperimentThree$handSwitch_actual = NA
  testData_ExperimentThree$coupletSwitch_actual = NA
  testData_ExperimentThree$fingerSwitch_actual = NA
  testData_ExperimentThree$respHand = NA
  testData_ExperimentThree$respCouplet = NA
  testData_ExperimentThree$corrHand = NA
  testData_ExperimentThree$corrCouplet = NA
  for(ai in 1:N_all){
    testData_ExperimentThree$zscoredRTs[testData_ExperimentThree$subject == subjNums_all[ai]] = scale(testData_ExperimentThree$rt[testData_ExperimentThree$subject == subjNums_all[ai]])
    testData_ExperimentThree$logRTs[testData_ExperimentThree$subject == subjNums_all[ai]] = log(testData_ExperimentThree$rt[testData_ExperimentThree$subject == subjNums_all[ai]])
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(testData_ExperimentThree$subject == subjNums_all[ai]&testData_ExperimentThree$corrrespAll == allResps[bi] & testData_ExperimentThree$phase == 'test')
      for (ci in 1:length(idx)){
        testData_ExperimentThree$stimNum[idx[ci]] = bi
        testData_ExperimentThree$iter[idx[ci]] = ci
      }
    }
    trialNum_idx = which(testData_ExperimentThree$subject == subjNums_all[ai] & testData_ExperimentThree$trialType == 'rl')
    testData_ExperimentThree$trialNum[trialNum_idx] = c(1:length(which(testData_ExperimentThree$subject == subjNums_all[ai] & testData_ExperimentThree$trialType == 'rl')))
  }
  for (xi in 1:dim(testData_ExperimentThree)[1]){
    # put in correct hand and couplet
    if(testData_ExperimentThree$corrresp[xi] %in% RH_new){
      testData_ExperimentThree$hand[xi] = 'R'
    }else if (testData_ExperimentThree$corrresp[xi] %in% LH_new){
      testData_ExperimentThree$hand[xi] = 'L'
    }
    
      if(testData_ExperimentThree$corrresp[xi] %in% coupletOne_new){
      testData_ExperimentThree$couplet[xi] = 1
    }else if (testData_ExperimentThree$corrresp[xi] %in% coupletTwo_new){
      testData_ExperimentThree$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(testData_ExperimentThree$key_press[xi] %in% RH_new){
      testData_ExperimentThree$respHand[xi] = 'R'
    }else if (testData_ExperimentThree$key_press[xi] %in% LH_new){
      testData_ExperimentThree$respHand[xi] = 'L'
    }
    
    if(testData_ExperimentThree$key_press[xi] %in% coupletOne_new){
      testData_ExperimentThree$respCouplet[xi] = 1
    }else if (testData_ExperimentThree$key_press[xi] %in% coupletTwo_new){
      testData_ExperimentThree$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(testData_ExperimentThree$respHand[xi])){
      testData_ExperimentThree$corrHand[xi] = 0
    } else if(testData_ExperimentThree$hand[xi] == testData_ExperimentThree$respHand[xi]){
      testData_ExperimentThree$corrHand[xi] = 1
    }else if (testData_ExperimentThree$hand[xi] != testData_ExperimentThree$respHand[xi]){
      testData_ExperimentThree$corrHand[xi] = 0
    }
     if(is.na(testData_ExperimentThree$respCouplet[xi])){
      testData_ExperimentThree$corrCouplet[xi] = 0
    }else if(testData_ExperimentThree$couplet[xi] == testData_ExperimentThree$respCouplet[xi]){
      testData_ExperimentThree$corrCouplet[xi] = 1
    }else if (testData_ExperimentThree$couplet[xi] != testData_ExperimentThree$respCouplet[xi]){
      testData_ExperimentThree$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(testData_ExperimentThree)[1]-1)){
    #hand switches
    if(testData_ExperimentThree$hand[di] == testData_ExperimentThree$hand[di+1]){
      testData_ExperimentThree$handSwitch[di+1]= 0
    } else if(testData_ExperimentThree$hand[di] != testData_ExperimentThree$hand[di+1]){
      testData_ExperimentThree$handSwitch[di+1] = 1
    }
    if(testData_ExperimentThree$couplet[di] == testData_ExperimentThree$couplet[di+1]){
      testData_ExperimentThree$coupletSwitch[di+1]= 0
    } else if(testData_ExperimentThree$couplet[di] != testData_ExperimentThree$couplet[di+1]){
      testData_ExperimentThree$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(testData_ExperimentThree$corrresp[di] == testData_ExperimentThree$corrresp[di+1]){
      testData_ExperimentThree$fingerSwitch[di+1] = 0
    }else{
      testData_ExperimentThree$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(testData_ExperimentThree$respHand[di]) | is.na(testData_ExperimentThree$respHand[di+1])){
      testData_ExperimentThree$handSwitch_actual[di]= NA
      testData_ExperimentThree$handSwitch_actual[di+1]=NA
    }else if(testData_ExperimentThree$respHand[di] == testData_ExperimentThree$respHand[di+1]){
      testData_ExperimentThree$handSwitch_actual[di+1]= 0
    } else if(testData_ExperimentThree$respHand[di] != testData_ExperimentThree$respHand[di+1]){
      testData_ExperimentThree$handSwitch_actual[di+1] = 1
    }
    if(is.na(testData_ExperimentThree$respCouplet[di]) | is.na(testData_ExperimentThree$respCouplet[di+1]) ){
      testData_ExperimentThree$coupletSwitch_actual[di]= NA
      testData_ExperimentThree$coupletSwitch_actual[di+1]= NA
    }else if(testData_ExperimentThree$respCouplet[di] == testData_ExperimentThree$respCouplet[di+1]){
      testData_ExperimentThree$coupletSwitch_actual[di+1]= 0
    } else if(testData_ExperimentThree$respCouplet[di] != testData_ExperimentThree$respCouplet[di+1]){
      testData_ExperimentThree$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(testData_ExperimentThree$key_press[di])| is.na(testData_ExperimentThree$key_press[di+1])){
      testData_ExperimentThree$fingerSwitch_actual[di+1]= NA
      testData_ExperimentThree$fingerSwitch_actual[di]= NA
    }else if(testData_ExperimentThree$key_press[di] == testData_ExperimentThree$key_press[di+1]){
      testData_ExperimentThree$fingerSwitch_actual[di+1] = 0
    }else{
      testData_ExperimentThree$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(testData_ExperimentThree$trialNum[di])){
      testData_ExperimentThree$handSwitch[di] = testData_ExperimentThree$handSwitch[di-1]
      testData_ExperimentThree$coupletSwitch[di] = testData_ExperimentThree$coupletSwitch[di-1]
      testData_ExperimentThree$fingerSwitch[di] = testData_ExperimentThree$fingerSwitch[di-1]
      testData_ExperimentThree$handSwitch_actual[di] = testData_ExperimentThree$handSwitch_actual[di-1]
      testData_ExperimentThree$coupletSwitch_actual[di] = testData_ExperimentThree$coupletSwitch_actual[di-1]
      testData_ExperimentThree$fingerSwitch_actual[di] = testData_ExperimentThree$fingerSwitch_actual[di-1]
    }else if(testData_ExperimentThree$trialNum[di] == 1){
      testData_ExperimentThree$handSwitch[di] = NA
      testData_ExperimentThree$coupletSwitch[di] = NA
      testData_ExperimentThree$fingerSwitch[di] = NA
            testData_ExperimentThree$handSwitch_actual[di] = NA
      testData_ExperimentThree$coupletSwitch_actual[di] = NA
      testData_ExperimentThree$fingerSwitch_actual[di] = NA
    }
  }
  testData_ExperimentThree$combinedType = NA
testData_ExperimentThree$combinedType[testData_ExperimentThree$coupletSwitch_actual == 0&testData_ExperimentThree$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentThree$combinedType[testData_ExperimentThree$coupletSwitch_actual == 0&testData_ExperimentThree$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentThree$combinedType[testData_ExperimentThree$coupletSwitch_actual == 1&testData_ExperimentThree$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentThree$combinedType[testData_ExperimentThree$coupletSwitch_actual == 1&testData_ExperimentThree$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentThree$combinedType[testData_ExperimentThree$fingerSwitch_actual == 0] = 'rep/rep/rep'

  # Fix issue with motorRepeat in postmotor phase classified in wrong phase
  repeatIdx = which(testData_ExperimentThree$trialType == 'motorRepeat')
  
  for(ei in repeatIdx){
    if(testData_ExperimentThree$phase[ei-1] == 'postmotor'){
      testData_ExperimentThree$phase[ei] = 'postmotor'
    }
  }

ExperimentThree = testData_ExperimentThree %>% filter(trialType == 'rl', iter < 128)

####### EXCLUSIONS #####
accuracyExclusions = ExperimentThree %>% group_by(subject, stimNum) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
#now filter for just these subjects that aren't excluded
testData_ExperimentThree_withExclusions = testData_ExperimentThree %>% filter(subject %in% subjNums_all[includeSub ==1])
# Add finger distance column 
testData_ExperimentThree_withExclusions$fingerDistance[1] = NA
testData_ExperimentThree_withExclusions$fingerDistance[2:length(testData_ExperimentThree_withExclusions$fingerDistance)] = abs(testData_ExperimentThree_withExclusions$finger_press[2:length(testData_ExperimentThree_withExclusions$fingerDistance)]-testData_ExperimentThree_withExclusions$finger_press[1:length(testData_ExperimentThree_withExclusions$finger_press)-1])
testData_ExperimentThree_withExclusions$fingerDistance[testData_ExperimentThree_withExclusions$trialNum == 1] = NA
# Add previous corr response column 
testData_ExperimentThree_withExclusions$corrrespAll_prev[1] = NA
testData_ExperimentThree_withExclusions$corrrespAll_prev[2:length(testData_ExperimentThree_withExclusions$corrresp)] = testData_ExperimentThree_withExclusions$corrrespAll[1:length(testData_ExperimentThree_withExclusions$corrresp)-1]
testData_ExperimentThree_withExclusions$corrrespAll_prev[testData_ExperimentThree_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
testData_ExperimentThree_withExclusions$finger_press_prev[1] = NA
testData_ExperimentThree_withExclusions$finger_press_prev[2:length(testData_ExperimentThree_withExclusions$finger_press)] = testData_ExperimentThree_withExclusions$finger_press[1:length(testData_ExperimentThree_withExclusions$corrresp)-1]
testData_ExperimentThree_withExclusions$finger_press_prev[testData_ExperimentThree_withExclusions$trialNum == 1] = NA

#add feature sw column
featureSwitchArray = array(c(0,1,1,2,1,2,2,3,1,0,2,1,2,1,3,2,1,2,0,1,2,3,1,2,2,1,1,0,3,2,2,1,1,2,2,3,0,1,1,2,2,1,3,2,1,0,2,1,2,3,1,2,1,2,0,1,3,2,2,1,2,1,1,0),dim = c(8,8))
testData_ExperimentThree_withExclusions$nFeatureSwitch[1] = NA
for(ai in 1:length(testData_ExperimentThree_withExclusions$nFeatureSwitch)){
  prev = testData_ExperimentThree_withExclusions$corrrespAll_prev[ai]
  curr = testData_ExperimentThree_withExclusions$corrrespAll[ai]
  testData_ExperimentThree_withExclusions$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
testData_ExperimentThree_withExclusions$nFeatureSwitch[testData_ExperimentThree_withExclusions$trialNum == 1] = NA

# MAKE SURE TO FILTER OUT EXTRA ITERATIONS! (move earlier in code for future versions)
ExperimentThree_withExclusions = testData_ExperimentThree_withExclusions %>% filter(phase == 'test') %>% filter(iter < 128)
## add switch/rep for each level of hierarchy
ExperimentThree_withExclusions$topType = NA
ExperimentThree_withExclusions$midType = NA
ExperimentThree_withExclusions$lowType = NA
#top level
ExperimentThree_withExclusions$topType[ExperimentThree_withExclusions$handSwitch ==1] = 1
ExperimentThree_withExclusions$topType[ExperimentThree_withExclusions$handSwitch ==0] = 0
#mid level
ExperimentThree_withExclusions$midType[ExperimentThree_withExclusions$coupletSwitch ==1] = 1
ExperimentThree_withExclusions$midType[ExperimentThree_withExclusions$coupletSwitch ==0] = 0
#low level
for(bi in 2:length(ExperimentThree_withExclusions$lowType)){
  prev = ExperimentThree_withExclusions$corrrespAll_prev[bi]
  curr = ExperimentThree_withExclusions$corrrespAll[bi]
  if(ExperimentThree_withExclusions$trialNum[bi] == 1){
   ExperimentThree_withExclusions$lowType[bi] = NA 
  }else if(((prev %% 2 == 0) & (curr %%2 == 0)) | ((prev %% 2 != 0) & (curr %% 2 != 0))){
    ExperimentThree_withExclusions$lowType[bi] = 0
  }else{
    ExperimentThree_withExclusions$lowType[bi] = 1
  }
}
ExperimentThree_withExclusions = ExperimentThree_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3))


##### MOTOR CORRECTION #####
allmotorData_withExclusions = testData_ExperimentThree_withExclusions %>% filter(phase %in% c('motor','postmotor'), corr == 1, trialType %in% c('motor','postmotor')) %>% group_by(subject, phase) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

motorStats = allmotorData_withExclusions %>% group_by(subject) %>% dplyr::summarise(avg = mean(rt,na.rm = TRUE),maxi = max(rt,na.rm = TRUE),mini = min(rt,na.rm =TRUE), trip = avg+3*sd(rt,na.rm = TRUE),tooFast = sum(rt < 150), tooSlow = sum(rt>900))

# do this in a hacky way rn to exclude super slow RTs
allmotorData_withExclusions$rtStrict = NA
allmotorData_withExclusions$rtStrict[allmotorData_withExclusions$rt < 900] = 1
allmotorData_withExclusions_corr = allmotorData_withExclusions %>% filter(trialType %in% c('motor','postmotor'), corr == 1, !is.na(fingerSwitch))
allmotorData_withExclusions_corr$rt_corr = allmotorData_withExclusions_corr$rt
allmotorData_withExclusions_corr$rtz_corr = allmotorData_withExclusions_corr$rtz

allmotorData_withExclusions_corr$rt_corr[allmotorData_withExclusions_corr$trialType == 'motorRepeat'] = NA
allmotorData_withExclusions_corr$rtz_corr[allmotorData_withExclusions_corr$trialType == 'motorRepeat'] = NA

# heatmap array for BOTH motor tasks
heatmapData_allTrials_resp_m_both = data.frame(subject = allmotorData_withExclusions_corr$subject[2:length(allmotorData_withExclusions_corr$subject)],currResp = allmotorData_withExclusions_corr$key_press[2:length(allmotorData_withExclusions_corr$key_press)], prevResp = allmotorData_withExclusions_corr$key_press[1:length(allmotorData_withExclusions_corr$key_press)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(76,75,74,72,70,68,83,65))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(65,83,68,70,72,74,75,76))

nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA
motorTransitions$rt = NA
motorTransitions$rt_both = NA
motorTransitions$rt_strict = NA
motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]

  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  }

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]

    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]

    motorTransitions$rt_strict[missingIdx[i]] = motorTransitions$rt_strict[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]

    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentThree_withExclusions$rt_corrected = NA
ExperimentThree_withExclusions$medRT_corrected = NA

ExperimentThree_withExclusions$rt_corrected_both = NA
ExperimentThree_withExclusions$medRT_corrected_both = NA

for(i in 1:length(ExperimentThree_withExclusions$rt_corrected)){
  if(ExperimentThree_withExclusions$trialNum[i] ==1){
    ExperimentThree_withExclusions$rt_corrected[i] = NA
  }else{
    prev = ExperimentThree_withExclusions$corrrespAll_prev[i]
    curr = ExperimentThree_withExclusions$finger_press[i]
    subj = ExperimentThree_withExclusions$subject[i]


    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr] & motorTransitions$subject == subj]

    
    ExperimentThree_withExclusions$rt_corrected_both[i] = ExperimentThree_withExclusions$rt[i] - motorRT_both
  }
}

#### STREAK TRIALS #####
ExperimentThree_withExclusions$streak = NA
ExperimentThree_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentThree_withExclusions$corr)){
  trial = ExperimentThree_withExclusions$trialNum[ai]
 if(ExperimentThree_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentThree_withExclusions$corr[ai]==1 & ExperimentThree_withExclusions$corr[ai-1]==1){
   ExperimentThree_withExclusions$streak[ai] = 1
   }else{
     ExperimentThree_withExclusions$streak[ai] = 0
   }
 }else{
   ExperimentThree_withExclusions$streak[ai] = 0
 }
}

for(ai in 2:length(ExperimentThree_withExclusions$corr)){
  trial = ExperimentThree_withExclusions$trialNum[ai]
 if(ExperimentThree_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentThree_withExclusions$streak[ai]==1 & ExperimentThree_withExclusions$streak[ai-1]==1){
   ExperimentThree_withExclusions$longStreak[ai] = 1
   }else{
     ExperimentThree_withExclusions$longStreak[ai] = 0
   }
 }else{
   ExperimentThree_withExclusions$longStreak[ai] = 0
 }
}
ExperimentThree_withExclusions$streak[ExperimentThree_withExclusions$trialNum ==1] = NA

######### WRITE DATA TO FILE ########
write.csv(allmotorData_withExclusions, 'motorData_Experiment3_compiled.csv')
write.csv(ExperimentThree_withExclusions, 'Experiment3_compiled.csv')

```
# Prep data for EXPERIMENT 4
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
# set up workspace
rm(list=ls(all=TRUE))
setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment4"
# load libraries
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(fabricatr)
library(Rmisc)
library(lme4)
library(rstatix)
library(MuMIn)

# read in data
    file_paths = fs::dir_ls(datadir)
  compiledData = data.frame()
  for (i in seq_along(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]])
    compiledData = rbind(compiledData, newSubjData)
  }
  
  # clean up data
  compiledData$rt = as.numeric(compiledData$rt)
  compiledData$time_elapsed = as.numeric(compiledData$time_elapsed)
  compiledData$key_press = as.numeric(compiledData$key_press)
  compiledData$stim = as.numeric(compiledData$stim)
  compiledData$corrresp = as.numeric(compiledData$corrresp)
  
  
  
  # sort data into prac and test
  compiledData = filter(compiledData, trialType %in% c('rl','motor','motorRepeat','postmotor'))
  pracData = filter(compiledData, phase == "prac")
  testData_ExperimentFour = filter(compiledData, phase %in% c("motor","test","postmotor"))
  
  # get some variables
  prolificNums = unique(testData_ExperimentFour$subject)
  subjNums_all = unique(testData_ExperimentFour$subject)
  N_all = length(prolificNums)
  
  allResps_new = c(65,83,68,70,72,74,75,76)
  LH_new = c(65,83,68,70)
  RH_new = c(72,74,75,76)
  coupletOne_new = c(65,83,72,74)
  coupletTwo_new = c(68,70,75,76)
  
  allResps = c(1,2,3,4,5,6,7,8)
  
  #make a column for recoded responses to make life easier
  
  testData_ExperimentFour$corrrespAll = NA
  testData_ExperimentFour$finger_press = NA
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 65] = 1
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 83] = 2
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 68] = 3
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 70] = 4
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 72] = 5
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 74] = 6
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 75] = 7
  testData_ExperimentFour$corrrespAll[testData_ExperimentFour$corrresp == 76] = 8
  
  testData_ExperimentFour$finger_press[ testData_ExperimentFour$key_press == 65] = 1
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 83] = 2
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 68] = 3
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 70] = 4
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 72] = 5
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 74] = 6
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 75] = 7
  testData_ExperimentFour$finger_press[testData_ExperimentFour$key_press == 76] = 8
  
  ns = length(allResps)
  # add more info to trials before saving
  testData_ExperimentFour$iter = NA
  testData_ExperimentFour$zscoredRTs = NA
  testData_ExperimentFour$logRTs = NA
  testData_ExperimentFour$hand = NA
  testData_ExperimentFour$couplet = NA
  testData_ExperimentFour$handSwitch = NA
  testData_ExperimentFour$coupletSwitch = NA
  testData_ExperimentFour$fingerSwitch = NA
  testData_ExperimentFour$handSwitch_actual = NA
  testData_ExperimentFour$coupletSwitch_actual = NA
  testData_ExperimentFour$fingerSwitch_actual = NA
  testData_ExperimentFour$respHand = NA
  testData_ExperimentFour$respCouplet = NA
  testData_ExperimentFour$corrHand = NA
  testData_ExperimentFour$corrCouplet = NA
  for(ai in 1:N_all){
    testData_ExperimentFour$zscoredRTs[testData_ExperimentFour$subject == subjNums_all[ai]] = scale(testData_ExperimentFour$rt[testData_ExperimentFour$subject == subjNums_all[ai]])
    testData_ExperimentFour$logRTs[testData_ExperimentFour$subject == subjNums_all[ai]] = log(testData_ExperimentFour$rt[testData_ExperimentFour$subject == subjNums_all[ai]])
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(testData_ExperimentFour$subject == subjNums_all[ai]&testData_ExperimentFour$corrrespAll == allResps[bi] & testData_ExperimentFour$phase == 'test')
      for (ci in 1:length(idx)){
        testData_ExperimentFour$stimNum[idx[ci]] = bi
        testData_ExperimentFour$iter[idx[ci]] = ci
      }
    }
    trialNum_idx = which(testData_ExperimentFour$subject == subjNums_all[ai] & testData_ExperimentFour$trialType == 'rl')
    testData_ExperimentFour$trialNum[trialNum_idx] = c(1:length(which(testData_ExperimentFour$subject == subjNums_all[ai] & testData_ExperimentFour$trialType == 'rl')))
  }
  for (xi in 1:dim(testData_ExperimentFour)[1]){
    # put in correct hand and couplet
    if(testData_ExperimentFour$corrresp[xi] %in% RH_new){
      testData_ExperimentFour$hand[xi] = 'R'
    }else if (testData_ExperimentFour$corrresp[xi] %in% LH_new){
      testData_ExperimentFour$hand[xi] = 'L'
    }
    
      if(testData_ExperimentFour$corrresp[xi] %in% coupletOne_new){
      testData_ExperimentFour$couplet[xi] = 1
    }else if (testData_ExperimentFour$corrresp[xi] %in% coupletTwo_new){
      testData_ExperimentFour$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(testData_ExperimentFour$key_press[xi] %in% RH_new){
      testData_ExperimentFour$respHand[xi] = 'R'
    }else if (testData_ExperimentFour$key_press[xi] %in% LH_new){
      testData_ExperimentFour$respHand[xi] = 'L'
    }
    
    if(testData_ExperimentFour$key_press[xi] %in% coupletOne_new){
      testData_ExperimentFour$respCouplet[xi] = 1
    }else if (testData_ExperimentFour$key_press[xi] %in% coupletTwo_new){
      testData_ExperimentFour$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(testData_ExperimentFour$respHand[xi])){
      testData_ExperimentFour$corrHand[xi] = 0
    } else if(testData_ExperimentFour$hand[xi] == testData_ExperimentFour$respHand[xi]){
      testData_ExperimentFour$corrHand[xi] = 1
    }else if (testData_ExperimentFour$hand[xi] != testData_ExperimentFour$respHand[xi]){
      testData_ExperimentFour$corrHand[xi] = 0
    }
     if(is.na(testData_ExperimentFour$respCouplet[xi])){
      testData_ExperimentFour$corrCouplet[xi] = 0
    }else if(testData_ExperimentFour$couplet[xi] == testData_ExperimentFour$respCouplet[xi]){
      testData_ExperimentFour$corrCouplet[xi] = 1
    }else if (testData_ExperimentFour$couplet[xi] != testData_ExperimentFour$respCouplet[xi]){
      testData_ExperimentFour$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(testData_ExperimentFour)[1]-1)){
    #hand switches
    if(testData_ExperimentFour$hand[di] == testData_ExperimentFour$hand[di+1]){
      testData_ExperimentFour$handSwitch[di+1]= 0
    } else if(testData_ExperimentFour$hand[di] != testData_ExperimentFour$hand[di+1]){
      testData_ExperimentFour$handSwitch[di+1] = 1
    }
    if(testData_ExperimentFour$couplet[di] == testData_ExperimentFour$couplet[di+1]){
      testData_ExperimentFour$coupletSwitch[di+1]= 0
    } else if(testData_ExperimentFour$couplet[di] != testData_ExperimentFour$couplet[di+1]){
      testData_ExperimentFour$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(testData_ExperimentFour$corrresp[di] == testData_ExperimentFour$corrresp[di+1]){
      testData_ExperimentFour$fingerSwitch[di+1] = 0
    }else{
      testData_ExperimentFour$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(testData_ExperimentFour$respHand[di]) | is.na(testData_ExperimentFour$respHand[di+1])){
      testData_ExperimentFour$handSwitch_actual[di]= NA
      testData_ExperimentFour$handSwitch_actual[di+1]=NA
    }else if(testData_ExperimentFour$respHand[di] == testData_ExperimentFour$respHand[di+1]){
      testData_ExperimentFour$handSwitch_actual[di+1]= 0
    } else if(testData_ExperimentFour$respHand[di] != testData_ExperimentFour$respHand[di+1]){
      testData_ExperimentFour$handSwitch_actual[di+1] = 1
    }
    if(is.na(testData_ExperimentFour$respCouplet[di]) | is.na(testData_ExperimentFour$respCouplet[di+1]) ){
      testData_ExperimentFour$coupletSwitch_actual[di]= NA
      testData_ExperimentFour$coupletSwitch_actual[di+1]= NA
    }else if(testData_ExperimentFour$respCouplet[di] == testData_ExperimentFour$respCouplet[di+1]){
      testData_ExperimentFour$coupletSwitch_actual[di+1]= 0
    } else if(testData_ExperimentFour$respCouplet[di] != testData_ExperimentFour$respCouplet[di+1]){
      testData_ExperimentFour$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(testData_ExperimentFour$key_press[di])| is.na(testData_ExperimentFour$key_press[di+1])){
      testData_ExperimentFour$fingerSwitch_actual[di+1]= NA
      testData_ExperimentFour$fingerSwitch_actual[di]= NA
    }else if(testData_ExperimentFour$key_press[di] == testData_ExperimentFour$key_press[di+1]){
      testData_ExperimentFour$fingerSwitch_actual[di+1] = 0
    }else{
      testData_ExperimentFour$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(testData_ExperimentFour$trialNum[di])){
      testData_ExperimentFour$handSwitch[di] = testData_ExperimentFour$handSwitch[di-1]
      testData_ExperimentFour$coupletSwitch[di] = testData_ExperimentFour$coupletSwitch[di-1]
      testData_ExperimentFour$fingerSwitch[di] = testData_ExperimentFour$fingerSwitch[di-1]
      testData_ExperimentFour$handSwitch_actual[di] = testData_ExperimentFour$handSwitch_actual[di-1]
      testData_ExperimentFour$coupletSwitch_actual[di] = testData_ExperimentFour$coupletSwitch_actual[di-1]
      testData_ExperimentFour$fingerSwitch_actual[di] = testData_ExperimentFour$fingerSwitch_actual[di-1]
    }else if(testData_ExperimentFour$trialNum[di] == 1){
      testData_ExperimentFour$handSwitch[di] = NA
      testData_ExperimentFour$coupletSwitch[di] = NA
      testData_ExperimentFour$fingerSwitch[di] = NA
      testData_ExperimentFour$handSwitch_actual[di] = NA
      testData_ExperimentFour$coupletSwitch_actual[di] = NA
      testData_ExperimentFour$fingerSwitch_actual[di] = NA
    }
  }

  testData_ExperimentFour$combinedType = NA
testData_ExperimentFour$combinedType[testData_ExperimentFour$coupletSwitch_actual == 0&testData_ExperimentFour$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentFour$combinedType[testData_ExperimentFour$coupletSwitch_actual == 0&testData_ExperimentFour$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentFour$combinedType[testData_ExperimentFour$coupletSwitch_actual == 1&testData_ExperimentFour$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentFour$combinedType[testData_ExperimentFour$coupletSwitch_actual == 1&testData_ExperimentFour$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentFour$combinedType[testData_ExperimentFour$fingerSwitch_actual == 0] = 'rep/rep/rep'
testData_ExperimentFour$combinedType[testData_ExperimentFour$trialNum == 1] = NA

testData_ExperimentFour$treeDistance = NA
testData_ExperimentFour$treeDistance[testData_ExperimentFour$coupletSwitch_actual == 0&testData_ExperimentFour$handSwitch_actual == 0] = 2
testData_ExperimentFour$treeDistance[testData_ExperimentFour$coupletSwitch_actual == 0&testData_ExperimentFour$handSwitch_actual == 1] = 6
testData_ExperimentFour$treeDistance[testData_ExperimentFour$coupletSwitch_actual == 1&testData_ExperimentFour$handSwitch_actual == 0] =4
testData_ExperimentFour$treeDistance[testData_ExperimentFour$coupletSwitch_actual == 1&testData_ExperimentFour$handSwitch_actual == 1] = 6
testData_ExperimentFour$treeDistance[testData_ExperimentFour$fingerSwitch_actual == 0] = 0
testData_ExperimentFour$treeDistance[testData_ExperimentFour$trialNum == 1] = NA

  # Fix issue with motorRepeat in postmotor phase classified in wrong phase
  repeatIdx = which(testData_ExperimentFour$trialType == 'motorRepeat')


# load in switch cost array 
featureSwArray_all = read_csv("~/Documents/GitHub/StructuredActionPrepVMDM/rawData/flatLearn_scrambled_nFeatureSw.csv")
ExperimentFour = testData_ExperimentFour %>% filter(trialType == 'rl', iter < 57)

###### EXCLUSIONS ######
accuracyExclusions = ExperimentFour %>% group_by(subject, stimNum) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
includeSub_strict = NA

for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) == 8){
    includeSub_strict[ai] = 1
  }else{
    includeSub_strict[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
subjNums_included_strict = subjNums_all[includeSub_strict ==1]
#now filter for just these subjects that aren't excluded 
testData_ExperimentFour_withExclusions = testData_ExperimentFour %>% filter(subject %in% subjNums_all[includeSub ==1])

#Add a column for the strict exclusion criterion to see if that helps
testData_ExperimentFour_withExclusions$includeStrict = NA
testData_ExperimentFour_withExclusions$includeStrict[testData_ExperimentFour_withExclusions$subject %in% c(subjNums_included_strict)] = 1

# Add finger distance column 
testData_ExperimentFour_withExclusions$fingerDistance[1] = NA
testData_ExperimentFour_withExclusions$fingerDistance[2:length(testData_ExperimentFour_withExclusions$fingerDistance)] = abs(testData_ExperimentFour_withExclusions$finger_press[2:length(testData_ExperimentFour_withExclusions$fingerDistance)]-testData_ExperimentFour_withExclusions$finger_press[1:length(testData_ExperimentFour_withExclusions$finger_press)-1])
testData_ExperimentFour_withExclusions$fingerDistance[testData_ExperimentFour_withExclusions$trialNum == 1] = NA
# Add previous corr response column 
testData_ExperimentFour_withExclusions$corrrespAll_prev[1] = NA
testData_ExperimentFour_withExclusions$corrrespAll_prev[2:length(testData_ExperimentFour_withExclusions$corrresp)] = testData_ExperimentFour_withExclusions$corrrespAll[1:length(testData_ExperimentFour_withExclusions$corrresp)-1]
testData_ExperimentFour_withExclusions$corrrespAll_prev[testData_ExperimentFour_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
testData_ExperimentFour_withExclusions$finger_press_prev[1] = NA
testData_ExperimentFour_withExclusions$finger_press_prev[2:length(testData_ExperimentFour_withExclusions$finger_press)] = testData_ExperimentFour_withExclusions$finger_press[1:length(testData_ExperimentFour_withExclusions$corrresp)-1]
testData_ExperimentFour_withExclusions$finger_press_prev[testData_ExperimentFour_withExclusions$trialNum == 1] = NA


treeDistanceArray = array(c(0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0,6,6,6,6,6,6,6,6,0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0),dim = c(8,8))
#add feature sw column
testData_ExperimentFour_withExclusions$nFeatureSwitch[1] = NA
for(ai in 1:length(testData_ExperimentFour_withExclusions$nFeatureSwitch)){
  subj = testData_ExperimentFour_withExclusions$subject[ai]
  featureSwArray_subj = array(featureSwArray_all[[subj]],dim = c(8,8))
  prev = testData_ExperimentFour_withExclusions$corrrespAll_prev[ai]
  curr = testData_ExperimentFour_withExclusions$corrrespAll[ai]
  testData_ExperimentFour_withExclusions$nFeatureSwitch[ai] = featureSwArray_subj[prev,curr]
}
testData_ExperimentFour_withExclusions$nFeatureSwitch[testData_ExperimentFour_withExclusions$trialNum == 1] = NA
testData_ExperimentFour_withExclusions = testData_ExperimentFour_withExclusions %>% filter(trialNum > 3)
ExperimentFour_withExclusions = testData_ExperimentFour_withExclusions %>% filter(trialType == 'rl')
## add switch/rep for each level of hierarchy
ExperimentFour_withExclusions$topType = NA
ExperimentFour_withExclusions$midType = NA
ExperimentFour_withExclusions$lowType = NA
#top level
ExperimentFour_withExclusions$topType[ExperimentFour_withExclusions$handSwitch ==1] = 1
ExperimentFour_withExclusions$topType[ExperimentFour_withExclusions$handSwitch ==0] = 0
#mid level
ExperimentFour_withExclusions$midType[ExperimentFour_withExclusions$coupletSwitch ==1] = 1
ExperimentFour_withExclusions$midType[ExperimentFour_withExclusions$coupletSwitch ==0] = 0

ExperimentFour_withExclusions = ExperimentFour_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)


#### MOTOR CORRECTION #####
motorData_withExclusions_allRT = testData_ExperimentFour_withExclusions %>% filter(phase == 'motor', trialType == 'motor', corr == 1) 
motorData_withExclusions = motorData_withExclusions_allRT %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)
motorUpperBound = mean(motorData_withExclusions_allRT$rt,na.rm = TRUE)+sd(motorData_withExclusions_allRT$rt,na.rm = TRUE)*3

motorStats = motorData_withExclusions %>% group_by(subject) %>% dplyr::summarise(avg = mean(rt,na.rm = TRUE),maxi = max(rt,na.rm = TRUE),mini = min(rt,na.rm =TRUE), trip = avg+3*sd(rt,na.rm = TRUE),tooFast = sum(rt < 150), tooSlow = sum(rt>motorUpperBound))

# do this in a hacky way rn to exclude super slow RTs
motorData_withExclusions$rtStrict = NA
motorData_withExclusions$rtStrict[motorData_withExclusions$rt < motorUpperBound] = 1


motorData_withExclusions_corr = motorData_withExclusions %>% filter(corr == 1)
motorData_withExclusions_corr$rt_corr[motorData_withExclusions_corr$trialType == 'motorRepeat'] = NA

heatmapData_allTrials_resp_m_both = data.frame(subject = motorData_withExclusions_corr$subject[2:length(motorData_withExclusions_corr$subject)],currResp = motorData_withExclusions_corr$key_press[2:length(motorData_withExclusions_corr$key_press)], prevResp = motorData_withExclusions_corr$key_press[1:length(motorData_withExclusions_corr$key_press)-1], trialNum = motorData_withExclusions_corr$trialNum[2:length(motorData_withExclusions_corr$trialNum)], rt = motorData_withExclusions_corr$rt[2:length(motorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(76,75,74,72,70,68,83,65))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(65,83,68,70,72,74,75,76))

nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA

motorTransitions$rt_both = NA
motorTransitions$medRT_both = NA

motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]

  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]


  }

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]
    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_both[missingIdx[i]] = motorTransitions$medRT_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentFour_withExclusions$rt_corrected_both = NA

ExperimentFour_withExclusions$rt_strict_corrected = NA

for(i in 1:length(ExperimentFour_withExclusions$rt_corrected_both)){
  if(ExperimentFour_withExclusions$trialNum[i] ==1){
    ExperimentFour_withExclusions$rt_corrected_both[i] = NA
  }else{
    prev = ExperimentFour_withExclusions$corrrespAll_prev[i]
    curr = ExperimentFour_withExclusions$finger_press[i]

    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]

    
    ExperimentFour_withExclusions$rt_corrected_both[i] = ExperimentFour_withExclusions$rt[i] - motorRT_both

  }
}
zscoredRT = ExperimentFour_withExclusions %>% group_by(subject) %>% dplyr::summarise(rt_corrected_both_z = scale(rt))
ExperimentFour_withExclusions$rt_corrected_both_z = zscoredRT$rt_corrected_both_z

##### STREAK TRIALS #####
ExperimentFour_withExclusions$streak = NA
ExperimentFour_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentFour_withExclusions$corr)){
  trial = ExperimentFour_withExclusions$trialNum[ai]
 if(ExperimentFour_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentFour_withExclusions$corr[ai]==1 & ExperimentFour_withExclusions$corr[ai-1]==1){
   ExperimentFour_withExclusions$streak[ai] = 1
   }else{
     ExperimentFour_withExclusions$streak[ai] = 0
   }
 }else{
   ExperimentFour_withExclusions$streak[ai] = 0
 }
}

for(ai in 2:length(ExperimentFour_withExclusions$corr)){
  trial = ExperimentFour_withExclusions$trialNum[ai]
 if(ExperimentFour_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentFour_withExclusions$streak[ai]==1 & ExperimentFour_withExclusions$streak[ai-1]==1){
   ExperimentFour_withExclusions$longStreak[ai] = 1
   }else{
     ExperimentFour_withExclusions$longStreak[ai] = 0
   }
 }else{
   ExperimentFour_withExclusions$longStreak[ai] = 0
 }
}
ExperimentFour_withExclusions$streak[ExperimentFour_withExclusions$trialNum ==1] = NA

######### WRITE DATA TO FILE ########
write.csv(motorData_withExclusions_corr, 'motorData_Experiment4_compiled.csv')
write.csv(ExperimentFour_withExclusions, 'Experiment4_compiled.csv')

```

# Prepare data for Experiment 5
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
## LEARNING DATA ##
rm(list=ls(all=TRUE))

setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment5/free"
# load libraries
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(fabricatr)
library(Rmisc)
library(lme4)
library(rstatix)
library(MuMIn)


# read in data
  file_paths = fs::dir_ls(datadir)
  compiledData = data.frame()
  for (i in seq_along(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]])
    compiledData = rbind(compiledData, newSubjData)
  }
  
  compiledData$subject[compiledData$subject]
  #set columns names to be closer to my normal code
  colnames(compiledData) = c('subject','group','taskType','block','trial','phase','stim','resp','corr','rtS','attemptNum','iter')


  # sort data into prac and test
  compiledData = filter(compiledData, phase %in% c('learn','motor'))
  testData_ExperimentFive = filter(compiledData, taskType %in% c("free"))
  
  # fix weird participant names
  testData_ExperimentFive$subject[testData_ExperimentFive$subject == '29a'] = '30'
  testData_ExperimentFive$subject[testData_ExperimentFive$subject == 'test'] = '33'
  
  # get some variables
  subjNums_all = unique(testData_ExperimentFive$subject)
  N_all = length(subjNums_all)
  
  allResps_new = c(1,2,3,4,5,6,7,8)
  LH_new = c(1,2,3,4)
  RH_new = c(5,6,7,8)
  
  # changed couplets to finger space
  coupletOne_new = c(1,2,5,6)
  coupletTwo_new = c(3,4,7,8)
  
  allResps = c(1,2,3,4,5,6,7,8)
  ns = length(allResps)
  # add more info to trials before saving
  testData_ExperimentFive$iter = NA
  testData_ExperimentFive$zscoredRTs = NA
  testData_ExperimentFive$logRTs = NA
  testData_ExperimentFive$hand = NA
  testData_ExperimentFive$couplet = NA
  testData_ExperimentFive$handSwitch = NA
  testData_ExperimentFive$coupletSwitch = NA
  testData_ExperimentFive$fingerSwitch = NA
  testData_ExperimentFive$handSwitch_actual = NA
  testData_ExperimentFive$coupletSwitch_actual = NA
  testData_ExperimentFive$fingerSwitch_actual = NA
  testData_ExperimentFive$respHand = NA
  testData_ExperimentFive$respCouplet = NA
  testData_ExperimentFive$corrHand = NA
  testData_ExperimentFive$corrCouplet = NA

  # Make a column of rt in ms
  testData_ExperimentFive$rt = testData_ExperimentFive$rtS * 1000
  # and a corrresp column
  testData_ExperimentFive$corrresp = testData_ExperimentFive$stim
  #and a trialNum one
  testData_ExperimentFive$trialNum = testData_ExperimentFive$trial
  for(ai in 1:N_all){
    testData_ExperimentFive$zscoredRTs[testData_ExperimentFive$subject == subjNums_all[ai]] = scale(testData_ExperimentFive$rt[testData_ExperimentFive$subject == subjNums_all[ai]])
    testData_ExperimentFive$logRTs[testData_ExperimentFive$subject == subjNums_all[ai]] = log(testData_ExperimentFive$rt[testData_ExperimentFive$subject == subjNums_all[ai]])
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(testData_ExperimentFive$subject == subjNums_all[ai]&testData_ExperimentFive$stim == allResps[bi] & testData_ExperimentFive$phase == 'learn')
      for (ci in 1:length(idx)){
        testData_ExperimentFive$iter[idx[ci]] = ci
      }
    }
  }
  for (xi in 1:dim(testData_ExperimentFive)[1]){
    # put in correct hand and couplet
    if(testData_ExperimentFive$stim[xi] %in% RH_new){
      testData_ExperimentFive$hand[xi] = 'R'
    }else if (testData_ExperimentFive$stim[xi] %in% LH_new){
      testData_ExperimentFive$hand[xi] = 'L'
    }
    
      if(testData_ExperimentFive$stim[xi] %in% coupletOne_new){
      testData_ExperimentFive$couplet[xi] = 1
    }else if (testData_ExperimentFive$stim[xi] %in% coupletTwo_new){
      testData_ExperimentFive$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(testData_ExperimentFive$resp[xi] %in% RH_new){
      testData_ExperimentFive$respHand[xi] = 'R'
    }else if (testData_ExperimentFive$resp[xi] %in% LH_new){
      testData_ExperimentFive$respHand[xi] = 'L'
    }
    
    if(testData_ExperimentFive$resp[xi] %in% coupletOne_new){
      testData_ExperimentFive$respCouplet[xi] = 1
    }else if (testData_ExperimentFive$resp[xi] %in% coupletTwo_new){
      testData_ExperimentFive$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(testData_ExperimentFive$respHand[xi])){
      testData_ExperimentFive$corrHand[xi] = 0
    } else if(testData_ExperimentFive$hand[xi] == testData_ExperimentFive$respHand[xi]){
      testData_ExperimentFive$corrHand[xi] = 1
    }else if (testData_ExperimentFive$hand[xi] != testData_ExperimentFive$respHand[xi]){
      testData_ExperimentFive$corrHand[xi] = 0
    }
     if(is.na(testData_ExperimentFive$respCouplet[xi])){
      testData_ExperimentFive$corrCouplet[xi] = 0
    }else if(testData_ExperimentFive$couplet[xi] == testData_ExperimentFive$respCouplet[xi]){
      testData_ExperimentFive$corrCouplet[xi] = 1
    }else if (testData_ExperimentFive$couplet[xi] != testData_ExperimentFive$respCouplet[xi]){
      testData_ExperimentFive$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(testData_ExperimentFive)[1]-1)){
    #hand switches
    if(testData_ExperimentFive$hand[di] == testData_ExperimentFive$hand[di+1]){
      testData_ExperimentFive$handSwitch[di+1]= 0
    } else if(testData_ExperimentFive$hand[di] != testData_ExperimentFive$hand[di+1]){
      testData_ExperimentFive$handSwitch[di+1] = 1
    }
    if(testData_ExperimentFive$couplet[di] == testData_ExperimentFive$couplet[di+1]){
      testData_ExperimentFive$coupletSwitch[di+1]= 0
    } else if(testData_ExperimentFive$couplet[di] != testData_ExperimentFive$couplet[di+1]){
      testData_ExperimentFive$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(testData_ExperimentFive$corrresp[di] == testData_ExperimentFive$corrresp[di+1]){
      testData_ExperimentFive$fingerSwitch[di+1] = 0
    }else{
      testData_ExperimentFive$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(testData_ExperimentFive$respHand[di]) | is.na(testData_ExperimentFive$respHand[di+1])){
      testData_ExperimentFive$handSwitch_actual[di]= NA
      testData_ExperimentFive$handSwitch_actual[di+1]=NA
    }else if(testData_ExperimentFive$respHand[di] == testData_ExperimentFive$respHand[di+1]){
      testData_ExperimentFive$handSwitch_actual[di+1]= 0
    } else if(testData_ExperimentFive$respHand[di] != testData_ExperimentFive$respHand[di+1]){
      testData_ExperimentFive$handSwitch_actual[di+1] = 1
    }
    if(is.na(testData_ExperimentFive$respCouplet[di]) | is.na(testData_ExperimentFive$respCouplet[di+1]) ){
      testData_ExperimentFive$coupletSwitch_actual[di]= NA
      testData_ExperimentFive$coupletSwitch_actual[di+1]= NA
    }else if(testData_ExperimentFive$respCouplet[di] == testData_ExperimentFive$respCouplet[di+1]){
      testData_ExperimentFive$coupletSwitch_actual[di+1]= 0
    } else if(testData_ExperimentFive$respCouplet[di] != testData_ExperimentFive$respCouplet[di+1]){
      testData_ExperimentFive$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(testData_ExperimentFive$resp[di])| is.na(testData_ExperimentFive$resp[di+1])){
      testData_ExperimentFive$fingerSwitch_actual[di+1]= NA
      testData_ExperimentFive$fingerSwitch_actual[di]= NA
    }else if(testData_ExperimentFive$resp[di] == testData_ExperimentFive$resp[di+1]){
      testData_ExperimentFive$fingerSwitch_actual[di+1] = 0
    }else{
      testData_ExperimentFive$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(testData_ExperimentFive$trial[di])){
      testData_ExperimentFive$handSwitch[di] = testData_ExperimentFive$handSwitch[di-1]
      testData_ExperimentFive$coupletSwitch[di] = testData_ExperimentFive$coupletSwitch[di-1]
      testData_ExperimentFive$fingerSwitch[di] = testData_ExperimentFive$fingerSwitch[di-1]
      testData_ExperimentFive$handSwitch_actual[di] = testData_ExperimentFive$handSwitch_actual[di-1]
      testData_ExperimentFive$coupletSwitch_actual[di] = testData_ExperimentFive$coupletSwitch_actual[di-1]
      testData_ExperimentFive$fingerSwitch_actual[di] = testData_ExperimentFive$fingerSwitch_actual[di-1]
    }else if(testData_ExperimentFive$trial[di] == 1){
      testData_ExperimentFive$handSwitch[di] = NA
      testData_ExperimentFive$coupletSwitch[di] = NA
      testData_ExperimentFive$fingerSwitch[di] = NA
            testData_ExperimentFive$handSwitch_actual[di] = NA
      testData_ExperimentFive$coupletSwitch_actual[di] = NA
      testData_ExperimentFive$fingerSwitch_actual[di] = NA
    }
  }
  testData_ExperimentFive$combinedType = NA
testData_ExperimentFive$combinedType[testData_ExperimentFive$coupletSwitch_actual == 0&testData_ExperimentFive$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentFive$combinedType[testData_ExperimentFive$coupletSwitch_actual == 0&testData_ExperimentFive$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentFive$combinedType[testData_ExperimentFive$coupletSwitch_actual == 1&testData_ExperimentFive$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentFive$combinedType[testData_ExperimentFive$coupletSwitch_actual == 1&testData_ExperimentFive$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentFive$combinedType[testData_ExperimentFive$fingerSwitch_actual == 0] = 'rep/rep/rep'
testData_ExperimentFive$combinedType[testData_ExperimentFive$trialNum == 1] = NA

  testData_ExperimentFive$treeDistance = NA
testData_ExperimentFive$treeDistance[testData_ExperimentFive$coupletSwitch_actual == 0&testData_ExperimentFive$handSwitch_actual == 0] = 2
testData_ExperimentFive$treeDistance[testData_ExperimentFive$coupletSwitch_actual == 0&testData_ExperimentFive$handSwitch_actual == 1] = 6
testData_ExperimentFive$treeDistance[testData_ExperimentFive$coupletSwitch_actual == 1&testData_ExperimentFive$handSwitch_actual == 0] =4
testData_ExperimentFive$treeDistance[testData_ExperimentFive$coupletSwitch_actual == 1&testData_ExperimentFive$handSwitch_actual == 1] = 6
testData_ExperimentFive$treeDistance[testData_ExperimentFive$fingerSwitch_actual == 0] = 0
testData_ExperimentFive$treeDistance[testData_ExperimentFive$trialNum == 1] = NA

ExperimentFive = testData_ExperimentFive %>% filter(phase == 'learn', iter < 56)

##### EXCLUSIONS #####
accuracyExclusions = ExperimentFive %>% group_by(subject, stim) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
includeSub_strict = NA

for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) == 8){
    includeSub_strict[ai] = 1
  }else{
    includeSub_strict[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
subjNums_included_strict = subjNums_all[includeSub_strict ==1]
#now filter for just these subjects that aren't excluded 
testData_ExperimentFive_withExclusions = testData_ExperimentFive %>% filter(subject %in% subjNums_all[includeSub ==1])

#Add a column for the strict exclusion criterion to see if that helps
testData_ExperimentFive_withExclusions$includeStrict = NA
testData_ExperimentFive_withExclusions$includeStrict[testData_ExperimentFive_withExclusions$subject %in% c(subjNums_included_strict)] = 1


# Add finger distance column 
testData_ExperimentFive_withExclusions$fingerDistance[1] = NA
testData_ExperimentFive_withExclusions$fingerDistance[2:length(testData_ExperimentFive_withExclusions$fingerDistance)] = abs(testData_ExperimentFive_withExclusions$resp[2:length(testData_ExperimentFive_withExclusions$fingerDistance)]-testData_ExperimentFive_withExclusions$resp[1:length(testData_ExperimentFive_withExclusions$fingerDistance)-1])
testData_ExperimentFive_withExclusions$fingerDistance[testData_ExperimentFive_withExclusions$trialNum == 1] = NA
# Add previous corr response column 
testData_ExperimentFive_withExclusions$corrrespAll_prev[1] = NA
testData_ExperimentFive_withExclusions$corrrespAll_prev[2:length(testData_ExperimentFive_withExclusions$stim)] = testData_ExperimentFive_withExclusions$stim[1:length(testData_ExperimentFive_withExclusions$stim)-1]
testData_ExperimentFive_withExclusions$corrrespAll_prev[testData_ExperimentFive_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
testData_ExperimentFive_withExclusions$finger_press_prev[1] = NA
testData_ExperimentFive_withExclusions$finger_press_prev[2:length(testData_ExperimentFive_withExclusions$resp)] = testData_ExperimentFive_withExclusions$resp[1:length(testData_ExperimentFive_withExclusions$stim)-1]
testData_ExperimentFive_withExclusions$finger_press_prev[testData_ExperimentFive_withExclusions$trialNum == 1] = NA

#add feature sw column
featureSwitchArray = array(c(0,1,1,2,1,2,2,3,1,0,2,1,2,1,3,2,1,2,0,1,2,3,1,2,2,1,1,0,3,2,2,1,1,2,2,3,0,1,1,2,2,1,3,2,1,0,2,1,2,3,1,2,1,2,0,1,3,2,2,1,2,1,1,0),dim = c(8,8))
treeDistanceArray = array(c(0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0,6,6,6,6,6,6,6,6,0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0),dim = c(8,8))

testData_ExperimentFive_withExclusions$nFeatureSwitch[1] = NA
for(ai in 1:length(testData_ExperimentFive_withExclusions$nFeatureSwitch)){
  prev = testData_ExperimentFive_withExclusions$corrrespAll_prev[ai]
  curr = testData_ExperimentFive_withExclusions$stim[ai]
  testData_ExperimentFive_withExclusions$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
testData_ExperimentFive_withExclusions$nFeatureSwitch[testData_ExperimentFive_withExclusions$trialNum == 1] = NA

ExperimentFive_withExclusions = testData_ExperimentFive_withExclusions %>% filter(phase == 'learn')
## add switch/rep for each level of hierarchy
ExperimentFive_withExclusions$topType = NA
ExperimentFive_withExclusions$midType = NA
ExperimentFive_withExclusions$lowType = NA
#top level
ExperimentFive_withExclusions$topType[ExperimentFive_withExclusions$handSwitch ==1] = 1
ExperimentFive_withExclusions$topType[ExperimentFive_withExclusions$handSwitch ==0] = 0
#mid level
ExperimentFive_withExclusions$midType[ExperimentFive_withExclusions$coupletSwitch ==1] = 1
ExperimentFive_withExclusions$midType[ExperimentFive_withExclusions$coupletSwitch ==0] = 0
#low level
for(bi in 2:length(ExperimentFive_withExclusions$lowType)){
  prev = ExperimentFive_withExclusions$corrrespAll_prev[bi]
  curr = ExperimentFive_withExclusions$stim[bi]
  if(ExperimentFive_withExclusions$trialNum[bi] == 1){
   ExperimentFive_withExclusions$lowType[bi] = NA 
  }else if(((prev %% 2 == 0) & (curr %%2 == 0)) | ((prev %% 2 != 0) & (curr %% 2 != 0))){
    ExperimentFive_withExclusions$lowType[bi] = 0
  }else{
    ExperimentFive_withExclusions$lowType[bi] = 1
  }
}

ExperimentFive_withExclusions$fifty = NA
pCorAll = ExperimentFive_withExclusions %>% group_by(subject) %>% dplyr::summarise(accu = mean(corr,na.rm = TRUE))
badSubs_accu = pCorAll$subject[pCorAll$accu<.5]
ExperimentFive_withExclusions$fifty[ExperimentFive_withExclusions$subject %in% badSubs_accu] = 1
ExperimentFive_withExclusions = ExperimentFive_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

###### MOTOR CORRECTION #####
allmotorData_withExclusions = testData_ExperimentFive_withExclusions %>% filter(phase %in% c('motor'), corr == 1, attemptNum == 1) %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)
motorUpperBound = mean(allmotorData_withExclusions$rt,na.rm = TRUE)+sd(allmotorData_withExclusions$rt,na.rm = TRUE)*3

motorStats = allmotorData_withExclusions %>% group_by(subject) %>% dplyr::summarise(avg = mean(rt,na.rm = TRUE),maxi = max(rt,na.rm = TRUE),mini = min(rt,na.rm =TRUE), trip = avg+3*sd(rt,na.rm = TRUE),tooFast = sum(rt < 150), tooSlow = sum(rt>900))

allmotorData_withExclusions = allmotorData_withExclusions %>% filter(rt < motorUpperBound)
# do this in a hacky way rn to exclude super slow RTs
allmotorData_withExclusions$rtStrict = NA
allmotorData_withExclusions$rtStrict[allmotorData_withExclusions$rt < 900] = 1
allmotorData_withExclusions_corr = allmotorData_withExclusions %>% filter(corr == 1, !is.na(fingerSwitch))
allmotorData_withExclusions_corr$rt_corr = allmotorData_withExclusions_corr$rt


# heatmap array for BOTH motor tasks
heatmapData_allTrials_resp_m_both = data.frame(subject = allmotorData_withExclusions_corr$subject[2:length(allmotorData_withExclusions_corr$subject)],currResp = allmotorData_withExclusions_corr$resp[2:length(allmotorData_withExclusions_corr$resp)], prevResp = allmotorData_withExclusions_corr$resp[1:length(allmotorData_withExclusions_corr$resp)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(1,2,3,4,5,6,7,8))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(8,7,6,5,4,3,2,1))

# ok, so we want add a column onto the main RL dataframe we're working with that has the baseline corrected rts
# first let's make the motor dataframe easier to use by creating a dataframe with all of the possible combinations
nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA

motorTransitions$rt_both = NA
motorTransitions$medRT_both = NA

motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]

  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  motorTransitions$medRT_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$medianRT[mi]


  }

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]
    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_both[missingIdx[i]] = motorTransitions$medRT_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentFive_withExclusions$rt_corrected_both = NA
ExperimentFive_withExclusions$medRT_corrected_both = NA

ExperimentFive_withExclusions$rt_strict_corrected = NA
ExperimentFive_withExclusions$medRT_strict_corrected = NA

for(i in 1:length(ExperimentFive_withExclusions$rt_corrected_both)){
  if(ExperimentFive_withExclusions$trialNum[i] ==1){
    ExperimentFive_withExclusions$rt_corrected[i] = NA
  }else{
    prev = ExperimentFive_withExclusions$finger_press_prev[i]
    curr = ExperimentFive_withExclusions$resp[i]

    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]
    motorRT_med_both = motorTransitions$medRT_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]

    
    ExperimentFive_withExclusions$rt_corrected_both[i] = ExperimentFive_withExclusions$rt[i] - motorRT_both
    ExperimentFive_withExclusions$medRT_corrected_both[i] = ExperimentFive_withExclusions$rt[i] - motorRT_med_both

  }
}


#### STREAK TRIALS #####
ExperimentFive_withExclusions$streak = NA
ExperimentFive_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentFive_withExclusions$corr)){
  trial = ExperimentFive_withExclusions$trialNum[ai]
 if(ExperimentFive_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentFive_withExclusions$corr[ai]==1 & ExperimentFive_withExclusions$corr[ai-1]==1){
   ExperimentFive_withExclusions$streak[ai] = 1
   }else{
     ExperimentFive_withExclusions$streak[ai] = 0
   }
 }else{
   ExperimentFive_withExclusions$streak[ai] = 0
 }
}

for(ai in 2:length(ExperimentFive_withExclusions$corr)){
  trial = ExperimentFive_withExclusions$trialNum[ai]
 if(ExperimentFive_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentFive_withExclusions$streak[ai]==1 & ExperimentFive_withExclusions$streak[ai-1]==1){
   ExperimentFive_withExclusions$longStreak[ai] = 1
   }else{
     ExperimentFive_withExclusions$longStreak[ai] = 0
   }
 }else{
   ExperimentFive_withExclusions$longStreak[ai] = 0
 }
}

ExperimentFive_withExclusions$streak[ExperimentFive_withExclusions$trialNum ==1] = NA

######### WRITE DATA TO FILE ########
write.csv(allmotorData_withExclusions, 'motorData_Experiment5_compiled.csv')
write.csv(ExperimentFive_withExclusions, 'Experiment5_learn_compiled.csv')
```

```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
## FORCED RESPONSE ##

#where is the data
forceddir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment5/forced"

# read in data
  file_paths = fs::dir_ls(forceddir)
  compiledData_forced = data.frame()
  for (i in 1:length(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]])
    compiledData_forced = rbind(compiledData_forced, newSubjData)
  }
  
  #set columns names to be closer to my normal code
  colnames(compiledData_forced) = c('subject','group','taskType','block','trial','phase','stim','resp','corr','timing','PT_planned','PT_actual','missed_stim_deadline')
  
  
  # sort data into prac and test
  ExperimentFive_forced = filter(compiledData_forced,phase == 'learn')

  # fix weird participant names
  ExperimentFive_forced$subject[ExperimentFive_forced$subject == '29a'] = '30'
  ExperimentFive_forced$subject[ExperimentFive_forced$subject == 'test'] = '33'

  # get some variables
  subjNums_forced = unique(ExperimentFive_forced$subject)
  N_all_forced = length(subjNums_forced)
  
  allResps_new = c(1,2,3,4,5,6,7,8)
  LH_new = c(1,2,3,4)
  RH_new = c(5,6,7,8)
  
  # changed couplets to finger space
  coupletOne_new = c(1,2,5,6)
  coupletTwo_new = c(3,4,7,8)
  
  allResps = c(1,2,3,4,5,6,7,8)
  ns = length(allResps)
  # add more info to trials before saving
  ExperimentFive_forced$iter = NA
  ExperimentFive_forced$hand = NA
  ExperimentFive_forced$couplet = NA
  ExperimentFive_forced$handSwitch = NA
  ExperimentFive_forced$coupletSwitch = NA
  ExperimentFive_forced$fingerSwitch = NA
  ExperimentFive_forced$handSwitch_actual = NA
  ExperimentFive_forced$coupletSwitch_actual = NA
  ExperimentFive_forced$fingerSwitch_actual = NA
  ExperimentFive_forced$respHand = NA
  ExperimentFive_forced$respCouplet = NA
  ExperimentFive_forced$corrHand = NA
  ExperimentFive_forced$corrCouplet = NA

  # and a corrresp column
  ExperimentFive_forced$corrresp = ExperimentFive_forced$stim
  #and a trialNum one
  ExperimentFive_forced$trialNum = ExperimentFive_forced$trial
  for(ai in 1:N_all){
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(ExperimentFive_forced$subject == subjNums_all[ai]&ExperimentFive_forced$stim == allResps[bi] & ExperimentFive_forced$phase == 'learn')
      for (ci in 1:length(idx)){
        ExperimentFive_forced$iter[idx[ci]] = ci
      }
    }
  }
  for (xi in 1:dim(ExperimentFive_forced)[1]){
    # put in correct hand and couplet
    if(ExperimentFive_forced$stim[xi] %in% RH_new){
      ExperimentFive_forced$hand[xi] = 'R'
    }else if (ExperimentFive_forced$stim[xi] %in% LH_new){
      ExperimentFive_forced$hand[xi] = 'L'
    }
    
      if(ExperimentFive_forced$stim[xi] %in% coupletOne_new){
      ExperimentFive_forced$couplet[xi] = 1
    }else if (ExperimentFive_forced$stim[xi] %in% coupletTwo_new){
      ExperimentFive_forced$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(ExperimentFive_forced$resp[xi] %in% RH_new){
      ExperimentFive_forced$respHand[xi] = 'R'
    }else if (ExperimentFive_forced$resp[xi] %in% LH_new){
      ExperimentFive_forced$respHand[xi] = 'L'
    }
    
    if(ExperimentFive_forced$resp[xi] %in% coupletOne_new){
      ExperimentFive_forced$respCouplet[xi] = 1
    }else if (ExperimentFive_forced$resp[xi] %in% coupletTwo_new){
      ExperimentFive_forced$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(ExperimentFive_forced$respHand[xi])){
      ExperimentFive_forced$corrHand[xi] = 0
    } else if(ExperimentFive_forced$hand[xi] == ExperimentFive_forced$respHand[xi]){
      ExperimentFive_forced$corrHand[xi] = 1
    }else if (ExperimentFive_forced$hand[xi] != ExperimentFive_forced$respHand[xi]){
      ExperimentFive_forced$corrHand[xi] = 0
    }
     if(is.na(ExperimentFive_forced$respCouplet[xi])){
      ExperimentFive_forced$corrCouplet[xi] = 0
    }else if(ExperimentFive_forced$couplet[xi] == ExperimentFive_forced$respCouplet[xi]){
      ExperimentFive_forced$corrCouplet[xi] = 1
    }else if (ExperimentFive_forced$couplet[xi] != ExperimentFive_forced$respCouplet[xi]){
      ExperimentFive_forced$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(ExperimentFive_forced)[1]-1)){
    #hand switches
    if(ExperimentFive_forced$hand[di] == ExperimentFive_forced$hand[di+1]){
      ExperimentFive_forced$handSwitch[di+1]= 0
    } else if(ExperimentFive_forced$hand[di] != ExperimentFive_forced$hand[di+1]){
      ExperimentFive_forced$handSwitch[di+1] = 1
    }
    if(ExperimentFive_forced$couplet[di] == ExperimentFive_forced$couplet[di+1]){
      ExperimentFive_forced$coupletSwitch[di+1]= 0
    } else if(ExperimentFive_forced$couplet[di] != ExperimentFive_forced$couplet[di+1]){
      ExperimentFive_forced$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(ExperimentFive_forced$corrresp[di] == ExperimentFive_forced$corrresp[di+1]){
      ExperimentFive_forced$fingerSwitch[di+1] = 0
    }else{
      ExperimentFive_forced$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(ExperimentFive_forced$respHand[di]) | is.na(ExperimentFive_forced$respHand[di+1])){
      ExperimentFive_forced$handSwitch_actual[di]= NA
      ExperimentFive_forced$handSwitch_actual[di+1]=NA
    }else if(ExperimentFive_forced$respHand[di] == ExperimentFive_forced$respHand[di+1]){
      ExperimentFive_forced$handSwitch_actual[di+1]= 0
    } else if(ExperimentFive_forced$respHand[di] != ExperimentFive_forced$respHand[di+1]){
      ExperimentFive_forced$handSwitch_actual[di+1] = 1
    }
    if(is.na(ExperimentFive_forced$respCouplet[di]) | is.na(ExperimentFive_forced$respCouplet[di+1]) ){
      ExperimentFive_forced$coupletSwitch_actual[di]= NA
      ExperimentFive_forced$coupletSwitch_actual[di+1]= NA
    }else if(ExperimentFive_forced$respCouplet[di] == ExperimentFive_forced$respCouplet[di+1]){
      ExperimentFive_forced$coupletSwitch_actual[di+1]= 0
    } else if(ExperimentFive_forced$respCouplet[di] != ExperimentFive_forced$respCouplet[di+1]){
      ExperimentFive_forced$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(ExperimentFive_forced$resp[di])| is.na(ExperimentFive_forced$resp[di+1])){
      ExperimentFive_forced$fingerSwitch_actual[di+1]= NA
      ExperimentFive_forced$fingerSwitch_actual[di]= NA
    }else if(ExperimentFive_forced$resp[di] == ExperimentFive_forced$resp[di+1]){
      ExperimentFive_forced$fingerSwitch_actual[di+1] = 0
    }else{
      ExperimentFive_forced$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(ExperimentFive_forced$trial[di])){
      ExperimentFive_forced$handSwitch[di] = ExperimentFive_forced$handSwitch[di-1]
      ExperimentFive_forced$coupletSwitch[di] = ExperimentFive_forced$coupletSwitch[di-1]
      ExperimentFive_forced$fingerSwitch[di] = ExperimentFive_forced$fingerSwitch[di-1]
      ExperimentFive_forced$handSwitch_actual[di] = ExperimentFive_forced$handSwitch_actual[di-1]
      ExperimentFive_forced$coupletSwitch_actual[di] = ExperimentFive_forced$coupletSwitch_actual[di-1]
      ExperimentFive_forced$fingerSwitch_actual[di] = ExperimentFive_forced$fingerSwitch_actual[di-1]
    }else if(ExperimentFive_forced$trial[di] == 1){
      ExperimentFive_forced$handSwitch[di] = NA
      ExperimentFive_forced$coupletSwitch[di] = NA
      ExperimentFive_forced$fingerSwitch[di] = NA
      ExperimentFive_forced$handSwitch_actual[di] = NA
      ExperimentFive_forced$coupletSwitch_actual[di] = NA
      ExperimentFive_forced$fingerSwitch_actual[di] = NA
    }
  }
  #first change the corr column to be more useful
ExperimentFive_forced$corr[ExperimentFive_forced$resp == ExperimentFive_forced$stim] = 1
ExperimentFive_forced$corr[ExperimentFive_forced$resp != ExperimentFive_forced$stim] = 0
ExperimentFive_forced$corr[is.na(ExperimentFive_forced$resp)] = NA

#calculate RTs
ExperimentFive_forced$rt = ExperimentFive_forced$PT_actual-ExperimentFive_forced$PT_planned

# filter out RTs that are too fast
ExperimentFive_forced = ExperimentFive_forced %>% filter(PT_actual >= 0)

# add bins for PT analyses
ExperimentFive_forced = ExperimentFive_forced %>% mutate(PT_actual_bins = split_quantile(PT_actual,12)) # ok weirdly 12 bins of one and 10 of the other whoops
ExperimentFive_forced = ExperimentFive_forced %>% mutate(PT_planned_bins = split_quantile(PT_planned,10))
 



ExperimentFive_forced$combinedType = NA
ExperimentFive_forced$combinedType[ExperimentFive_forced$coupletSwitch_actual == 0&ExperimentFive_forced$handSwitch_actual == 0] = 'rep/rep/sw'
ExperimentFive_forced$combinedType[ExperimentFive_forced$coupletSwitch_actual == 0&ExperimentFive_forced$handSwitch_actual == 1] = 'sw/rep/sw'
ExperimentFive_forced$combinedType[ExperimentFive_forced$coupletSwitch_actual == 1&ExperimentFive_forced$handSwitch_actual == 0] = 'rep/sw/sw'
ExperimentFive_forced$combinedType[ExperimentFive_forced$coupletSwitch_actual == 1&ExperimentFive_forced$handSwitch_actual == 1] = 'sw/sw/sw'
ExperimentFive_forced$combinedType[ExperimentFive_forced$fingerSwitch_actual == 0] = 'rep/rep/rep'
ExperimentFive_forced$combinedType[ExperimentFive_forced$trialNum == 1] = NA

  ExperimentFive_forced$treeDistance = NA
ExperimentFive_forced$treeDistance[ExperimentFive_forced$coupletSwitch_actual == 0&ExperimentFive_forced$handSwitch_actual == 0] = 2
ExperimentFive_forced$treeDistance[ExperimentFive_forced$coupletSwitch_actual == 0&ExperimentFive_forced$handSwitch_actual == 1] = 6
ExperimentFive_forced$treeDistance[ExperimentFive_forced$coupletSwitch_actual == 1&ExperimentFive_forced$handSwitch_actual == 0] =4
ExperimentFive_forced$treeDistance[ExperimentFive_forced$coupletSwitch_actual == 1&ExperimentFive_forced$handSwitch_actual == 1] = 6
ExperimentFive_forced$treeDistance[ExperimentFive_forced$fingerSwitch_actual == 0] = 0
ExperimentFive_forced$treeDistance[ExperimentFive_forced$trialNum == 1] = NA

ExperimentFive_forced$corrresp_prev = NA
ExperimentFive_forced$corrresp_prev[2:length(ExperimentFive_forced$corrresp_prev)] = ExperimentFive_forced$corrresp[1:(length(ExperimentFive_forced$corrresp_prev)-1)]
featureSwitchArray = array(c(0,1,1,2,3,2,2,1, 
                             1,0,2,1,2,3,1,2,
                             1,2,0,1,2,1,3,2,
                             2,1,1,0,1,2,2,3,
                             3,2,2,1,0,1,1,2,
                             2,3,1,2,1,0,2,1,
                             2,1,3,2,1,2,0,1,
                             1,2,2,3,2,1,1,0),dim = c(8,8))
ExperimentFive_forced$nFeatureSwitch[1] = NA
for(ai in 1:length(ExperimentFive_forced$nFeatureSwitch)){
  prev = ExperimentFive_forced$corrresp_prev[ai]
  curr = ExperimentFive_forced$corrresp[ai]
  ExperimentFive_forced$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
ExperimentFive_forced$nFeatureSwitch[ExperimentFive_forced$trialNum == 1] = NA

# Add column for error type
ExperimentFive_forced$errorType = NA
ExperimentFive_forced$errorType[ExperimentFive_forced$corr == 1] = '1/1/1'
ExperimentFive_forced$errorType[ExperimentFive_forced$corr == 0 & ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 1] = '1/1/0'
ExperimentFive_forced$errorType[ExperimentFive_forced$corr == 0 & ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 0] = '1/0/0'
ExperimentFive_forced$errorType[ExperimentFive_forced$corr == 0 & ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 1] = '0/1/0'
ExperimentFive_forced$errorType[ExperimentFive_forced$corr == 0 & ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 0] = '0/0/0'

#set up corr finger column
ExperimentFive_forced$corrFinger = NA
ExperimentFive_forced$corrFinger[ExperimentFive_forced$corrresp %in% c(1,3,5,7) & ExperimentFive_forced$resp %in% c(1,3,5,7)] = 1
ExperimentFive_forced$corrFinger[ExperimentFive_forced$corrresp %in% c(2,4,6,8) & ExperimentFive_forced$resp %in% c(2,4,6,8)] = 1
ExperimentFive_forced$corrFinger[ExperimentFive_forced$corrresp %in% c(1,3,5,7) & ExperimentFive_forced$resp %in% c(2,4,6,8)] = 0
ExperimentFive_forced$corrFinger[ExperimentFive_forced$corrresp %in% c(2,4,6,8) & ExperimentFive_forced$resp %in% c(1,3,5,7)] = 0

ExperimentFive_forced$errorType2 = NA
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 1 & ExperimentFive_forced$corrFinger == 1] = '1/1/1'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 1 & ExperimentFive_forced$corrFinger == 0] = '1/1/0'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 0 & ExperimentFive_forced$corrFinger == 1] = '1/0/1'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 1 & ExperimentFive_forced$corrCouplet == 0 & ExperimentFive_forced$corrFinger == 0] = '1/0/0'

ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 1 & ExperimentFive_forced$corrFinger == 1] = '0/1/1'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 1 & ExperimentFive_forced$corrFinger == 0] = '0/1/0'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 0 & ExperimentFive_forced$corrFinger == 1] = '0/0/1'
ExperimentFive_forced$errorType2[ExperimentFive_forced$corrHand == 0 & ExperimentFive_forced$corrCouplet == 0 & ExperimentFive_forced$corrFinger == 0] = '0/0/0'


#convert what you need into factors to stop from droppipng in groups
ExperimentFive_forced$subject = as.factor(ExperimentFive_forced$subject)
ExperimentFive_forced$errorType = as.factor(ExperimentFive_forced$errorType)
ExperimentFive_forced$treeDistance = as.factor(ExperimentFive_forced$treeDistance)
ExperimentFive_forced$PT_actual_bins = as.factor(ExperimentFive_forced$PT_actual_bins)
ExperimentFive_forced$PT_planned_bins = as.factor(ExperimentFive_forced$PT_planned_bins)
ExperimentFive_forced$combinedType = as.factor(ExperimentFive_forced$combinedType)

### Exclusions ####
# mark subjects that shoudl be inlcuded from the learnign sample
ExperimentFive_forced$includeLearn = NA
ExperimentFive_forced$includeLearn[ExperimentFive_forced$subject %in% subjNums_included] = 1

ExperimentFive_forced$timing_chill = NA
ExperimentFive_forced$timing_chill[abs(ExperimentFive_forced$rt)<=.25] = 1


# filter out PT_actual of over 1.75s
ExperimentFive_forced_withExclusions = ExperimentFive_forced %>% filter(PT_actual <= 1.75, includeLearn == 1)

## Add bins of PTs
#method one
ExperimentFive_forced_withExclusions$eml = NA
ExperimentFive_forced_withExclusions$eml[ExperimentFive_forced_withExclusions$PT_actual <= .4] = 'a_early'
ExperimentFive_forced_withExclusions$eml[ExperimentFive_forced_withExclusions$PT_actual > .4 & ExperimentFive_forced_withExclusions$PT_actual <= .8] = 'b_mid'
ExperimentFive_forced_withExclusions$eml[ExperimentFive_forced_withExclusions$PT_actual > .8] = 'c_late'
#method 2
ExperimentFive_forced_withExclusions$eml2 = NA
ExperimentFive_forced_withExclusions$eml2[ExperimentFive_forced_withExclusions$PT_actual <= .5] = 'a_early'
ExperimentFive_forced_withExclusions$eml2[ExperimentFive_forced_withExclusions$PT_actual > .5 & ExperimentFive_forced_withExclusions$PT_actual <= .9] = 'b_mid'
ExperimentFive_forced_withExclusions$eml2[ExperimentFive_forced_withExclusions$PT_actual > .9] = 'c_late'
# method 3
ExperimentFive_forced_withExclusions$eml3 = NA
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual <= .3] = 'a_early1'
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual  > .3 & ExperimentFive_forced_withExclusions$PT_actual <= .5] = 'a_early2'
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual > .5 & ExperimentFive_forced_withExclusions$PT_actual <= .7] = 'b_mid1'
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual > .7 & ExperimentFive_forced_withExclusions$PT_actual <= .9] = 'b_mid2'
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual > .9& ExperimentFive_forced_withExclusions$PT_actual <= 1.1] = 'c_late1'
ExperimentFive_forced_withExclusions$eml3[ExperimentFive_forced_withExclusions$PT_actual > 1.1] = 'c_late2'


ExperimentFive_forced_withExclusions$corrFinger = NA
ExperimentFive_forced_withExclusions$corrFinger[ExperimentFive_forced_withExclusions$corrresp %in% c(1,3,5,7) & ExperimentFive_forced_withExclusions$resp %in% c(1,3,5,7)] = 1
ExperimentFive_forced_withExclusions$corrFinger[ExperimentFive_forced_withExclusions$corrresp %in% c(2,4,6,8) & ExperimentFive_forced_withExclusions$resp %in% c(2,4,6,8)] = 1
ExperimentFive_forced_withExclusions$corrFinger[ExperimentFive_forced_withExclusions$corrresp %in% c(1,3,5,7) & ExperimentFive_forced_withExclusions$resp %in% c(2,4,6,8)] = 0
ExperimentFive_forced_withExclusions$corrFinger[ExperimentFive_forced_withExclusions$corrresp %in% c(2,4,6,8) & ExperimentFive_forced_withExclusions$resp %in% c(1,3,5,7)] = 0

ExperimentFive_forced_withExclusions$errorType2 = NA
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 1 & ExperimentFive_forced_withExclusions$corrCouplet == 1 & ExperimentFive_forced_withExclusions$corrFinger == 1] = '1/1/1'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 1 & ExperimentFive_forced_withExclusions$corrCouplet == 1 & ExperimentFive_forced_withExclusions$corrFinger == 0] = '1/1/0'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 1 & ExperimentFive_forced_withExclusions$corrCouplet == 0 & ExperimentFive_forced_withExclusions$corrFinger == 1] = '1/0/1'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 1 & ExperimentFive_forced_withExclusions$corrCouplet == 0 & ExperimentFive_forced_withExclusions$corrFinger == 0] = '1/0/0'

ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 0 & ExperimentFive_forced_withExclusions$corrCouplet == 1 & ExperimentFive_forced_withExclusions$corrFinger == 1] = '0/1/1'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 0 & ExperimentFive_forced_withExclusions$corrCouplet == 1 & ExperimentFive_forced_withExclusions$corrFinger == 0] = '0/1/0'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 0 & ExperimentFive_forced_withExclusions$corrCouplet == 0 & ExperimentFive_forced_withExclusions$corrFinger == 1] = '0/0/1'
ExperimentFive_forced_withExclusions$errorType2[ExperimentFive_forced_withExclusions$corrHand == 0 & ExperimentFive_forced_withExclusions$corrCouplet == 0 & ExperimentFive_forced_withExclusions$corrFinger == 0] = '0/0/0'

ExperimentFive_forced_withExclusions$errorType2 = as.factor(ExperimentFive_forced_withExclusions$errorType2)

######### WRITE DATA TO FILE ########
write.csv(ExperimentFive_forced_withExclusions, 'Experiment5_forced_compiled.csv')
```
# Prepare data for EXPERIMENT 6
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
## LEARN DATA ##
rm(list=ls(all=TRUE))
setwd("~/Documents/GitHub/StructuredActionPrepVMDM/rawData")
datadir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment6/free"

# load libraries
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(reshape2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(itsadug)
library(RColorBrewer)
library(knitr)
library(extrafont)
library(fs)
library(fabricatr)
library(Rmisc)
library(lme4)
library(rstatix)
library(MuMIn)

  file_paths = fs::dir_ls(datadir)
  compiledData = data.frame()
  for (i in seq_along(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]])
    compiledData = rbind(compiledData, newSubjData)
  }
  
  compiledData$subject[compiledData$subject]
  #set columns names to be closer to my normal code
  colnames(compiledData) = c('subject','group','taskType','block','trial','phase','stim','resp','corr','rtS','attemptNum','iter')


  # sort data into prac and test
  compiledData = filter(compiledData, phase %in% c('learn','motor'))
  testData_ExperimentSix = filter(compiledData, taskType %in% c("free"))
  
  # get some variables
  subjNums_all = unique(testData_ExperimentSix$subject)
  N_all = length(subjNums_all)
  
  allResps_new = c(1,2,3,4,5,6,7,8)
  LH_new = c(1,2,3,4)
  RH_new = c(5,6,7,8)
  
  # changed couplets to finger space
  coupletOne_new = c(1,2,5,6)
  coupletTwo_new = c(3,4,7,8)
  
  allResps = c(1,2,3,4,5,6,7,8)
  ns = length(allResps)
  # add more info to trials before saving
  testData_ExperimentSix$iter = NA
  testData_ExperimentSix$zscoredRTs = NA
  testData_ExperimentSix$logRTs = NA
  testData_ExperimentSix$hand = NA
  testData_ExperimentSix$couplet = NA
  testData_ExperimentSix$handSwitch = NA
  testData_ExperimentSix$coupletSwitch = NA
  testData_ExperimentSix$fingerSwitch = NA
  testData_ExperimentSix$handSwitch_actual = NA
  testData_ExperimentSix$coupletSwitch_actual = NA
  testData_ExperimentSix$fingerSwitch_actual = NA
  testData_ExperimentSix$respHand = NA
  testData_ExperimentSix$respCouplet = NA
  testData_ExperimentSix$corrHand = NA
  testData_ExperimentSix$corrCouplet = NA

  # Make a column of rt in ms
  testData_ExperimentSix$rt = testData_ExperimentSix$rtS * 1000
  # and a corrresp column
  testData_ExperimentSix$corrresp = testData_ExperimentSix$stim
  #and a trialNum one
  testData_ExperimentSix$trialNum = testData_ExperimentSix$trial
  for(ai in 1:N_all){
    testData_ExperimentSix$zscoredRTs[testData_ExperimentSix$subject == subjNums_all[ai]] = scale(testData_ExperimentSix$rt[testData_ExperimentSix$subject == subjNums_all[ai]])
    testData_ExperimentSix$logRTs[testData_ExperimentSix$subject == subjNums_all[ai]] = log(testData_ExperimentSix$rt[testData_ExperimentSix$subject == subjNums_all[ai]])
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(testData_ExperimentSix$subject == subjNums_all[ai]&testData_ExperimentSix$stim == allResps[bi] & testData_ExperimentSix$phase == 'learn')
      for (ci in 1:length(idx)){
        testData_ExperimentSix$iter[idx[ci]] = ci
      }
    }
  }
  for (xi in 1:dim(testData_ExperimentSix)[1]){
    # put in correct hand and couplet
    if(testData_ExperimentSix$stim[xi] %in% RH_new){
      testData_ExperimentSix$hand[xi] = 'R'
    }else if (testData_ExperimentSix$stim[xi] %in% LH_new){
      testData_ExperimentSix$hand[xi] = 'L'
    }
    
      if(testData_ExperimentSix$stim[xi] %in% coupletOne_new){
      testData_ExperimentSix$couplet[xi] = 1
    }else if (testData_ExperimentSix$stim[xi] %in% coupletTwo_new){
      testData_ExperimentSix$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(testData_ExperimentSix$resp[xi] %in% RH_new){
      testData_ExperimentSix$respHand[xi] = 'R'
    }else if (testData_ExperimentSix$resp[xi] %in% LH_new){
      testData_ExperimentSix$respHand[xi] = 'L'
    }
    
    if(testData_ExperimentSix$resp[xi] %in% coupletOne_new){
      testData_ExperimentSix$respCouplet[xi] = 1
    }else if (testData_ExperimentSix$resp[xi] %in% coupletTwo_new){
      testData_ExperimentSix$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(testData_ExperimentSix$respHand[xi])){
      testData_ExperimentSix$corrHand[xi] = 0
    } else if(testData_ExperimentSix$hand[xi] == testData_ExperimentSix$respHand[xi]){
      testData_ExperimentSix$corrHand[xi] = 1
    }else if (testData_ExperimentSix$hand[xi] != testData_ExperimentSix$respHand[xi]){
      testData_ExperimentSix$corrHand[xi] = 0
    }
     if(is.na(testData_ExperimentSix$respCouplet[xi])){
      testData_ExperimentSix$corrCouplet[xi] = 0
    }else if(testData_ExperimentSix$couplet[xi] == testData_ExperimentSix$respCouplet[xi]){
      testData_ExperimentSix$corrCouplet[xi] = 1
    }else if (testData_ExperimentSix$couplet[xi] != testData_ExperimentSix$respCouplet[xi]){
      testData_ExperimentSix$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(testData_ExperimentSix)[1]-1)){
    #hand switches
    if(testData_ExperimentSix$hand[di] == testData_ExperimentSix$hand[di+1]){
      testData_ExperimentSix$handSwitch[di+1]= 0
    } else if(testData_ExperimentSix$hand[di] != testData_ExperimentSix$hand[di+1]){
      testData_ExperimentSix$handSwitch[di+1] = 1
    }
    if(testData_ExperimentSix$couplet[di] == testData_ExperimentSix$couplet[di+1]){
      testData_ExperimentSix$coupletSwitch[di+1]= 0
    } else if(testData_ExperimentSix$couplet[di] != testData_ExperimentSix$couplet[di+1]){
      testData_ExperimentSix$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(testData_ExperimentSix$corrresp[di] == testData_ExperimentSix$corrresp[di+1]){
      testData_ExperimentSix$fingerSwitch[di+1] = 0
    }else{
      testData_ExperimentSix$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(testData_ExperimentSix$respHand[di]) | is.na(testData_ExperimentSix$respHand[di+1])){
      testData_ExperimentSix$handSwitch_actual[di]= NA
      testData_ExperimentSix$handSwitch_actual[di+1]=NA
    }else if(testData_ExperimentSix$respHand[di] == testData_ExperimentSix$respHand[di+1]){
      testData_ExperimentSix$handSwitch_actual[di+1]= 0
    } else if(testData_ExperimentSix$respHand[di] != testData_ExperimentSix$respHand[di+1]){
      testData_ExperimentSix$handSwitch_actual[di+1] = 1
    }
    if(is.na(testData_ExperimentSix$respCouplet[di]) | is.na(testData_ExperimentSix$respCouplet[di+1]) ){
      testData_ExperimentSix$coupletSwitch_actual[di]= NA
      testData_ExperimentSix$coupletSwitch_actual[di+1]= NA
    }else if(testData_ExperimentSix$respCouplet[di] == testData_ExperimentSix$respCouplet[di+1]){
      testData_ExperimentSix$coupletSwitch_actual[di+1]= 0
    } else if(testData_ExperimentSix$respCouplet[di] != testData_ExperimentSix$respCouplet[di+1]){
      testData_ExperimentSix$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(testData_ExperimentSix$resp[di])| is.na(testData_ExperimentSix$resp[di+1])){
      testData_ExperimentSix$fingerSwitch_actual[di+1]= NA
      testData_ExperimentSix$fingerSwitch_actual[di]= NA
    }else if(testData_ExperimentSix$resp[di] == testData_ExperimentSix$resp[di+1]){
      testData_ExperimentSix$fingerSwitch_actual[di+1] = 0
    }else{
      testData_ExperimentSix$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(testData_ExperimentSix$trial[di])){
      testData_ExperimentSix$handSwitch[di] = testData_ExperimentSix$handSwitch[di-1]
      testData_ExperimentSix$coupletSwitch[di] = testData_ExperimentSix$coupletSwitch[di-1]
      testData_ExperimentSix$fingerSwitch[di] = testData_ExperimentSix$fingerSwitch[di-1]
      testData_ExperimentSix$handSwitch_actual[di] = testData_ExperimentSix$handSwitch_actual[di-1]
      testData_ExperimentSix$coupletSwitch_actual[di] = testData_ExperimentSix$coupletSwitch_actual[di-1]
      testData_ExperimentSix$fingerSwitch_actual[di] = testData_ExperimentSix$fingerSwitch_actual[di-1]
    }else if(testData_ExperimentSix$trial[di] == 1){
      testData_ExperimentSix$handSwitch[di] = NA
      testData_ExperimentSix$coupletSwitch[di] = NA
      testData_ExperimentSix$fingerSwitch[di] = NA
            testData_ExperimentSix$handSwitch_actual[di] = NA
      testData_ExperimentSix$coupletSwitch_actual[di] = NA
      testData_ExperimentSix$fingerSwitch_actual[di] = NA
    }
  }
  testData_ExperimentSix$combinedType = NA
testData_ExperimentSix$combinedType[testData_ExperimentSix$coupletSwitch_actual == 0&testData_ExperimentSix$handSwitch_actual == 0] = 'rep/rep/sw'
testData_ExperimentSix$combinedType[testData_ExperimentSix$coupletSwitch_actual == 0&testData_ExperimentSix$handSwitch_actual == 1] = 'sw/rep/sw'
testData_ExperimentSix$combinedType[testData_ExperimentSix$coupletSwitch_actual == 1&testData_ExperimentSix$handSwitch_actual == 0] = 'rep/sw/sw'
testData_ExperimentSix$combinedType[testData_ExperimentSix$coupletSwitch_actual == 1&testData_ExperimentSix$handSwitch_actual == 1] = 'sw/sw/sw'
testData_ExperimentSix$combinedType[testData_ExperimentSix$fingerSwitch_actual == 0] = 'rep/rep/rep'
testData_ExperimentSix$combinedType[testData_ExperimentSix$trialNum == 1] = NA

  testData_ExperimentSix$treeDistance = NA
testData_ExperimentSix$treeDistance[testData_ExperimentSix$coupletSwitch_actual == 0&testData_ExperimentSix$handSwitch_actual == 0] = 2
testData_ExperimentSix$treeDistance[testData_ExperimentSix$coupletSwitch_actual == 0&testData_ExperimentSix$handSwitch_actual == 1] = 6
testData_ExperimentSix$treeDistance[testData_ExperimentSix$coupletSwitch_actual == 1&testData_ExperimentSix$handSwitch_actual == 0] =4
testData_ExperimentSix$treeDistance[testData_ExperimentSix$coupletSwitch_actual == 1&testData_ExperimentSix$handSwitch_actual == 1] = 6
testData_ExperimentSix$treeDistance[testData_ExperimentSix$fingerSwitch_actual == 0] = 0
testData_ExperimentSix$treeDistance[testData_ExperimentSix$trialNum == 1] = NA

ExperimentSix = testData_ExperimentSix %>% filter(phase == 'learn', iter < 56)

#### EXCLUSIONS ####

accuracyExclusions = ExperimentSix %>% group_by(subject, stim) %>% dplyr::summarize(pCorStim = mean(corr,na.rm = TRUE))

includeSub = NA
includeSub_strict = NA

for (ai in 1:length(subjNums_all)){
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) >4){
    includeSub[ai] = 1
  }else{
    includeSub[ai] = 0
  }
  if(sum(accuracyExclusions$pCorStim[accuracyExclusions$subject == subjNums_all[ai]] >=.25) == 8){
    includeSub_strict[ai] = 1
  }else{
    includeSub_strict[ai] = 0
  }
}
subjNums_included = subjNums_all[includeSub ==1]
subjNums_included_strict = subjNums_all[includeSub_strict ==1]
#now filter for just these subjects that aren't excluded 
testData_ExperimentSix_withExclusions = testData_ExperimentSix %>% filter(subject %in% subjNums_all[includeSub ==1])

#Add a column for the strict exclusion criterion to see if that helps
testData_ExperimentSix_withExclusions$includeStrict = NA
testData_ExperimentSix_withExclusions$includeStrict[testData_ExperimentSix_withExclusions$subject %in% c(subjNums_included_strict)] = 1


# Add finger distance column 
testData_ExperimentSix_withExclusions$fingerDistance[1] = NA
testData_ExperimentSix_withExclusions$fingerDistance[2:length(testData_ExperimentSix_withExclusions$fingerDistance)] = abs(testData_ExperimentSix_withExclusions$resp[2:length(testData_ExperimentSix_withExclusions$fingerDistance)]-testData_ExperimentSix_withExclusions$resp[1:length(testData_ExperimentSix_withExclusions$fingerDistance)-1])
testData_ExperimentSix_withExclusions$fingerDistance[testData_ExperimentSix_withExclusions$trialNum == 1] = NA
# Add previous corr response column 
testData_ExperimentSix_withExclusions$corrrespAll_prev[1] = NA
testData_ExperimentSix_withExclusions$corrrespAll_prev[2:length(testData_ExperimentSix_withExclusions$stim)] = testData_ExperimentSix_withExclusions$stim[1:length(testData_ExperimentSix_withExclusions$stim)-1]
testData_ExperimentSix_withExclusions$corrrespAll_prev[testData_ExperimentSix_withExclusions$trialNum == 1] = NA
# Add previous ACTUAL response column 
testData_ExperimentSix_withExclusions$finger_press_prev[1] = NA
testData_ExperimentSix_withExclusions$finger_press_prev[2:length(testData_ExperimentSix_withExclusions$resp)] = testData_ExperimentSix_withExclusions$resp[1:length(testData_ExperimentSix_withExclusions$stim)-1]
testData_ExperimentSix_withExclusions$finger_press_prev[testData_ExperimentSix_withExclusions$trialNum == 1] = NA

#add feature sw column
featureSwitchArray = array(c(0,1,1,2,1,2,2,3,1,0,2,1,2,1,3,2,1,2,0,1,2,3,1,2,2,1,1,0,3,2,2,1,1,2,2,3,0,1,1,2,2,1,3,2,1,0,2,1,2,3,1,2,1,2,0,1,3,2,2,1,2,1,1,0),dim = c(8,8))
treeDistanceArray = array(c(0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0,6,6,6,6,6,6,6,6,0,2,4,4,6,6,6,6,2,0,4,4,6,6,6,6,4,4,0,2,6,6,6,6,4,4,2,0),dim = c(8,8))

testData_ExperimentSix_withExclusions$nFeatureSwitch[1] = NA
for(ai in 1:length(testData_ExperimentSix_withExclusions$nFeatureSwitch)){
  prev = testData_ExperimentSix_withExclusions$corrrespAll_prev[ai]
  curr = testData_ExperimentSix_withExclusions$stim[ai]
  testData_ExperimentSix_withExclusions$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
testData_ExperimentSix_withExclusions$nFeatureSwitch[testData_ExperimentSix_withExclusions$trialNum == 1] = NA

ExperimentSix_withExclusions = testData_ExperimentSix_withExclusions %>% filter(phase == 'learn')

## add switch/rep for each level of hierarchy
ExperimentSix_withExclusions$topType = NA
ExperimentSix_withExclusions$midType = NA
ExperimentSix_withExclusions$lowType = NA
#top level
ExperimentSix_withExclusions$topType[ExperimentSix_withExclusions$handSwitch ==1] = 1
ExperimentSix_withExclusions$topType[ExperimentSix_withExclusions$handSwitch ==0] = 0
#mid level
ExperimentSix_withExclusions$midType[ExperimentSix_withExclusions$coupletSwitch ==1] = 1
ExperimentSix_withExclusions$midType[ExperimentSix_withExclusions$coupletSwitch ==0] = 0
#low level
for(bi in 2:length(ExperimentSix_withExclusions$lowType)){
  prev = ExperimentSix_withExclusions$corrrespAll_prev[bi]
  curr = ExperimentSix_withExclusions$stim[bi]
  if(ExperimentSix_withExclusions$trialNum[bi] == 1){
   ExperimentSix_withExclusions$lowType[bi] = NA 
  }else if(((prev %% 2 == 0) & (curr %%2 == 0)) | ((prev %% 2 != 0) & (curr %% 2 != 0))){
    ExperimentSix_withExclusions$lowType[bi] = 0
  }else{
    ExperimentSix_withExclusions$lowType[bi] = 1
  }
}

ExperimentSix_withExclusions$fifty = NA
pCorAll = ExperimentSix_withExclusions %>% group_by(subject) %>% dplyr::summarise(accu = mean(corr,na.rm = TRUE))
badSubs_accu = pCorAll$subject[pCorAll$accu<.5]
ExperimentSix_withExclusions$fifty[ExperimentSix_withExclusions$subject %in% badSubs_accu] = 1

ExperimentSix_withExclusions = ExperimentSix_withExclusions %>% group_by(subject) %>% filter(rt > 200, rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)

#### MOTOR CORRECTION ####
allmotorData_withExclusions = testData_ExperimentSix_withExclusions %>% filter(phase %in% c('motor'), corr == 1, attemptNum == 1) %>% group_by(subject) %>% filter(rt > mean(rt,na.rm = TRUE)-(sd(rt,na.rm = TRUE) * 3),rt < mean(rt,na.rm = TRUE)+(sd(rt,na.rm = TRUE) * 3), trialNum > 3)
motorUpperBound = mean(allmotorData_withExclusions$rt,na.rm = TRUE)+sd(allmotorData_withExclusions$rt,na.rm = TRUE)*3

motorStats = allmotorData_withExclusions %>% group_by(subject) %>% dplyr::summarise(avg = mean(rt,na.rm = TRUE),maxi = max(rt,na.rm = TRUE),mini = min(rt,na.rm =TRUE), trip = avg+3*sd(rt,na.rm = TRUE),tooFast = sum(rt < 150), tooSlow = sum(rt>900))

allmotorData_withExclusions = allmotorData_withExclusions %>% filter(rt < motorUpperBound)

allmotorData_withExclusions$rtStrict = NA
allmotorData_withExclusions$rtStrict[allmotorData_withExclusions$rt < 900] = 1

allmotorData_withExclusions_corr = allmotorData_withExclusions %>% filter(corr == 1, !is.na(fingerSwitch))
allmotorData_withExclusions_corr$rt_corr = allmotorData_withExclusions_corr$rt

heatmapData_allTrials_resp_m_both = data.frame(subject = allmotorData_withExclusions_corr$subject[2:length(allmotorData_withExclusions_corr$subject)],currResp = allmotorData_withExclusions_corr$resp[2:length(allmotorData_withExclusions_corr$resp)], prevResp = allmotorData_withExclusions_corr$resp[1:length(allmotorData_withExclusions_corr$resp)-1], trialNum = allmotorData_withExclusions_corr$trialNum[2:length(allmotorData_withExclusions_corr$trialNum)], rt = allmotorData_withExclusions_corr$rt_corr[2:length(allmotorData_withExclusions_corr$rt_corr)]) %>% filter(trialNum > 3, !is.na(currResp), !is.na(prevResp)) %>% group_by(subject,currResp, prevResp) %>% dplyr::summarize(meanRT = mean(rt, na.rm=TRUE),medianRT = median(rt, na.rm = TRUE))
heatmapData_allTrials_resp_m_both$prevResp = factor(heatmapData_allTrials_resp_m_both$prevResp, levels = c(1,2,3,4,5,6,7,8))
heatmapData_allTrials_resp_m_both$currResp = factor(heatmapData_allTrials_resp_m_both$currResp, levels = c(8,7,6,5,4,3,2,1))

nCombos = ns^2
motorTransitions = data.frame(matrix(nrow = nCombos*length(subjNums_included)))

#initialize these columns
motorTransitions$subject = NA
motorTransitions$currResp = NA
motorTransitions$prevResp = NA

motorTransitions$rt_both = NA
motorTransitions$medRT_both = NA

motorTransitions$swapRT = NA

#loop over subjects to set up empty array
startidx = 1
for(xi in 1:length(subjNums_included)){
  motorTransitions$subject[startidx:(startidx+nCombos-1)] = subjNums_included[xi]
  counter = startidx
  for(yi in 1:ns){
    for(zi in 1:ns){
      motorTransitions$currResp[counter] = allResps_new[yi]
      motorTransitions$prevResp[counter] = allResps_new[zi]
      counter = counter+1
    }
  }
  startidx = counter
}

# now put in the meanrts from the motor task
for(mi in 1:dim(heatmapData_allTrials_resp_m_both)[1]){
  subj = heatmapData_allTrials_resp_m_both$subject[mi]
  currResp_m = heatmapData_allTrials_resp_m_both$currResp[mi]
  prevResp_m = heatmapData_allTrials_resp_m_both$prevResp[mi]

  motorTransitions$rt_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$meanRT[mi]
  motorTransitions$medRT_both[motorTransitions$subject == subj & motorTransitions$currResp == currResp_m & motorTransitions$prevResp == prevResp_m] = heatmapData_allTrials_resp_m_both$medianRT[mi]


  }

# if there are missing transitions from the motor sequence, fill in with the transition in the opposite direction
missingIdx = which(is.na(motorTransitions$rt))
if(sum(missingIdx) != 0){
  for(i in 1:length(missingIdx)){
    swapPrev = motorTransitions$currResp[missingIdx[i]]
    swapCurr = motorTransitions$prevResp[missingIdx[i]]
    motorTransitions$rt_both[missingIdx[i]] = motorTransitions$rt_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$medRT_both[missingIdx[i]] = motorTransitions$medRT_both[motorTransitions$currResp == swapPrev & motorTransitions$prevResp == swapCurr]
    motorTransitions$swapRT[missingIdx[i]] = 1
  }
}

ExperimentSix_withExclusions$rt_corrected_both = NA
ExperimentSix_withExclusions$medRT_corrected_both = NA

ExperimentSix_withExclusions$rt_strict_corrected = NA
ExperimentSix_withExclusions$medRT_strict_corrected = NA

for(i in 1:length(ExperimentSix_withExclusions$rt_corrected_both)){
  if(ExperimentSix_withExclusions$trialNum[i] ==1){
    ExperimentSix_withExclusions$rt_corrected[i] = NA
  }else{
    prev = ExperimentSix_withExclusions$finger_press_prev[i]
    curr = ExperimentSix_withExclusions$resp[i]

    motorRT_both = motorTransitions$rt_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]
    motorRT_med_both = motorTransitions$medRT_both[motorTransitions$prevResp == allResps_new[prev] & motorTransitions$currResp == allResps_new[curr]]

    
    ExperimentSix_withExclusions$rt_corrected_both[i] = ExperimentSix_withExclusions$rt[i] - motorRT_both
    ExperimentSix_withExclusions$medRT_corrected_both[i] = ExperimentSix_withExclusions$rt[i] - motorRT_med_both

  }
}


#### STREAK TRIALS ####
ExperimentSix_withExclusions$streak = NA
ExperimentSix_withExclusions$longStreak = NA
for(ai in 2:length(ExperimentSix_withExclusions$corr)){
  trial = ExperimentSix_withExclusions$trialNum[ai]
 if(ExperimentSix_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentSix_withExclusions$corr[ai]==1 & ExperimentSix_withExclusions$corr[ai-1]==1){
   ExperimentSix_withExclusions$streak[ai] = 1
   }else{
     ExperimentSix_withExclusions$streak[ai] = 0
   }
 }else{
   ExperimentSix_withExclusions$streak[ai] = 0
 }
}

for(ai in 2:length(ExperimentSix_withExclusions$corr)){
  trial = ExperimentSix_withExclusions$trialNum[ai]
 if(ExperimentSix_withExclusions$trialNum[ai-1]==(trial-1)){
   if(ExperimentSix_withExclusions$streak[ai]==1 & ExperimentSix_withExclusions$streak[ai-1]==1){
   ExperimentSix_withExclusions$longStreak[ai] = 1
   }else{
     ExperimentSix_withExclusions$longStreak[ai] = 0
   }
 }else{
   ExperimentSix_withExclusions$longStreak[ai] = 0
 }
}

ExperimentSix_withExclusions$streak[ExperimentSix_withExclusions$trialNum ==1] = NA

######### WRITE DATA TO FILE ########
write.csv(allmotorData_withExclusions_corr, 'motorData_Experiment6_compiled.csv')
write.csv(ExperimentSix_withExclusions, 'Experiment6_learn_compiled.csv')

```

\newpage
# FORCED RT ANALYSES
```{r, echo=F, message=F, warning=F, error=T, fig.width=6, fig.height=4, fig.align='center'}
## FORCED RESPONSE
#where is the data
forceddir = "~/Documents/GitHub/StructuredActionPrepVMDM/rawData/Experiment6/forced"

# read in data
  file_paths = fs::dir_ls(forceddir)
  compiledData_forced = data.frame()
  for (i in 1:length(file_paths)){
    newSubjData = read_csv(file = file_paths[[i]])
    compiledData_forced = rbind(compiledData_forced, newSubjData)
  }
  
  #set columns names to be closer to my normal code
  colnames(compiledData_forced) = c('subject','group','taskType','block','trial','phase','stim','resp','corr','timing','PT_planned','PT_actual','missed_stim_deadline')
  
  
  # sort data into prac and test
  ExperimentSix_forced = filter(compiledData_forced,phase == 'learn')

  # get some variables
  subjNums_forced = unique(ExperimentSix_forced$subject)
  N_all_forced = length(subjNums_forced)
  
  allResps_new = c(1,2,3,4,5,6,7,8)
  LH_new = c(1,2,3,4)
  RH_new = c(5,6,7,8)
  
  # changed couplets to finger space
  coupletOne_new = c(1,2,5,6)
  coupletTwo_new = c(3,4,7,8)
  
  allResps = c(1,2,3,4,5,6,7,8)
  ns = length(allResps)
  # add more info to trials before saving
  ExperimentSix_forced$iter = NA
  ExperimentSix_forced$hand = NA
  ExperimentSix_forced$couplet = NA
  ExperimentSix_forced$handSwitch = NA
  ExperimentSix_forced$coupletSwitch = NA
  ExperimentSix_forced$fingerSwitch = NA
  ExperimentSix_forced$handSwitch_actual = NA
  ExperimentSix_forced$coupletSwitch_actual = NA
  ExperimentSix_forced$fingerSwitch_actual = NA
  ExperimentSix_forced$respHand = NA
  ExperimentSix_forced$respCouplet = NA
  ExperimentSix_forced$corrHand = NA
  ExperimentSix_forced$corrCouplet = NA

  # and a corrresp column
  ExperimentSix_forced$corrresp = ExperimentSix_forced$stim
  #and a trialNum one
  ExperimentSix_forced$trialNum = ExperimentSix_forced$trial
  for(ai in 1:N_all){
    # add iteration numbers
    for(bi in 1:ns){
      idx = which(ExperimentSix_forced$subject == subjNums_all[ai]&ExperimentSix_forced$stim == allResps[bi] & ExperimentSix_forced$phase == 'learn')
      for (ci in 1:length(idx)){
        ExperimentSix_forced$iter[idx[ci]] = ci
      }
    }
  }
  for (xi in 1:dim(ExperimentSix_forced)[1]){
    # put in correct hand and couplet
    if(ExperimentSix_forced$stim[xi] %in% RH_new){
      ExperimentSix_forced$hand[xi] = 'R'
    }else if (ExperimentSix_forced$stim[xi] %in% LH_new){
      ExperimentSix_forced$hand[xi] = 'L'
    }
    
      if(ExperimentSix_forced$stim[xi] %in% coupletOne_new){
      ExperimentSix_forced$couplet[xi] = 1
    }else if (ExperimentSix_forced$stim[xi] %in% coupletTwo_new){
      ExperimentSix_forced$couplet[xi] = 2
    }
    
    # put in the hand and couplet of the response
    if(ExperimentSix_forced$resp[xi] %in% RH_new){
      ExperimentSix_forced$respHand[xi] = 'R'
    }else if (ExperimentSix_forced$resp[xi] %in% LH_new){
      ExperimentSix_forced$respHand[xi] = 'L'
    }
    
    if(ExperimentSix_forced$resp[xi] %in% coupletOne_new){
      ExperimentSix_forced$respCouplet[xi] = 1
    }else if (ExperimentSix_forced$resp[xi] %in% coupletTwo_new){
      ExperimentSix_forced$respCouplet[xi] = 2
    }
    
    # 1 for correct hand, 0 for incorrect
    if(is.na(ExperimentSix_forced$respHand[xi])){
      ExperimentSix_forced$corrHand[xi] = 0
    } else if(ExperimentSix_forced$hand[xi] == ExperimentSix_forced$respHand[xi]){
      ExperimentSix_forced$corrHand[xi] = 1
    }else if (ExperimentSix_forced$hand[xi] != ExperimentSix_forced$respHand[xi]){
      ExperimentSix_forced$corrHand[xi] = 0
    }
     if(is.na(ExperimentSix_forced$respCouplet[xi])){
      ExperimentSix_forced$corrCouplet[xi] = 0
    }else if(ExperimentSix_forced$couplet[xi] == ExperimentSix_forced$respCouplet[xi]){
      ExperimentSix_forced$corrCouplet[xi] = 1
    }else if (ExperimentSix_forced$couplet[xi] != ExperimentSix_forced$respCouplet[xi]){
      ExperimentSix_forced$corrCouplet[xi] = 0
    }
    
  }
  
  for(di in 1:(dim(ExperimentSix_forced)[1]-1)){
    #hand switches
    if(ExperimentSix_forced$hand[di] == ExperimentSix_forced$hand[di+1]){
      ExperimentSix_forced$handSwitch[di+1]= 0
    } else if(ExperimentSix_forced$hand[di] != ExperimentSix_forced$hand[di+1]){
      ExperimentSix_forced$handSwitch[di+1] = 1
    }
    if(ExperimentSix_forced$couplet[di] == ExperimentSix_forced$couplet[di+1]){
      ExperimentSix_forced$coupletSwitch[di+1]= 0
    } else if(ExperimentSix_forced$couplet[di] != ExperimentSix_forced$couplet[di+1]){
      ExperimentSix_forced$coupletSwitch[di+1] = 1
    }
    #switches and repeats for finger
    if(ExperimentSix_forced$corrresp[di] == ExperimentSix_forced$corrresp[di+1]){
      ExperimentSix_forced$fingerSwitch[di+1] = 0
    }else{
      ExperimentSix_forced$fingerSwitch[di+1] = 1
    }
    
    # same but with actual responses
    if(is.na(ExperimentSix_forced$respHand[di]) | is.na(ExperimentSix_forced$respHand[di+1])){
      ExperimentSix_forced$handSwitch_actual[di]= NA
      ExperimentSix_forced$handSwitch_actual[di+1]=NA
    }else if(ExperimentSix_forced$respHand[di] == ExperimentSix_forced$respHand[di+1]){
      ExperimentSix_forced$handSwitch_actual[di+1]= 0
    } else if(ExperimentSix_forced$respHand[di] != ExperimentSix_forced$respHand[di+1]){
      ExperimentSix_forced$handSwitch_actual[di+1] = 1
    }
    if(is.na(ExperimentSix_forced$respCouplet[di]) | is.na(ExperimentSix_forced$respCouplet[di+1]) ){
      ExperimentSix_forced$coupletSwitch_actual[di]= NA
      ExperimentSix_forced$coupletSwitch_actual[di+1]= NA
    }else if(ExperimentSix_forced$respCouplet[di] == ExperimentSix_forced$respCouplet[di+1]){
      ExperimentSix_forced$coupletSwitch_actual[di+1]= 0
    } else if(ExperimentSix_forced$respCouplet[di] != ExperimentSix_forced$respCouplet[di+1]){
      ExperimentSix_forced$coupletSwitch_actual[di+1] = 1
    }
    #switches and repeats for finger
    if(is.na(ExperimentSix_forced$resp[di])| is.na(ExperimentSix_forced$resp[di+1])){
      ExperimentSix_forced$fingerSwitch_actual[di+1]= NA
      ExperimentSix_forced$fingerSwitch_actual[di]= NA
    }else if(ExperimentSix_forced$resp[di] == ExperimentSix_forced$resp[di+1]){
      ExperimentSix_forced$fingerSwitch_actual[di+1] = 0
    }else{
      ExperimentSix_forced$fingerSwitch_actual[di+1] = 1
    }
    
    if(is.na(ExperimentSix_forced$trial[di])){
      ExperimentSix_forced$handSwitch[di] = ExperimentSix_forced$handSwitch[di-1]
      ExperimentSix_forced$coupletSwitch[di] = ExperimentSix_forced$coupletSwitch[di-1]
      ExperimentSix_forced$fingerSwitch[di] = ExperimentSix_forced$fingerSwitch[di-1]
      ExperimentSix_forced$handSwitch_actual[di] = ExperimentSix_forced$handSwitch_actual[di-1]
      ExperimentSix_forced$coupletSwitch_actual[di] = ExperimentSix_forced$coupletSwitch_actual[di-1]
      ExperimentSix_forced$fingerSwitch_actual[di] = ExperimentSix_forced$fingerSwitch_actual[di-1]
    }else if(ExperimentSix_forced$trial[di] == 1){
      ExperimentSix_forced$handSwitch[di] = NA
      ExperimentSix_forced$coupletSwitch[di] = NA
      ExperimentSix_forced$fingerSwitch[di] = NA
      ExperimentSix_forced$handSwitch_actual[di] = NA
      ExperimentSix_forced$coupletSwitch_actual[di] = NA
      ExperimentSix_forced$fingerSwitch_actual[di] = NA
    }
  }
  #first change the corr column to be more useful
ExperimentSix_forced$corr[ExperimentSix_forced$resp == ExperimentSix_forced$stim] = 1
ExperimentSix_forced$corr[ExperimentSix_forced$resp != ExperimentSix_forced$stim] = 0
ExperimentSix_forced$corr[is.na(ExperimentSix_forced$resp)] = NA

#calculate RTs
ExperimentSix_forced$rt = ExperimentSix_forced$PT_actual-ExperimentSix_forced$PT_planned

# filter out RTs that are too fast
ExperimentSix_forced = ExperimentSix_forced %>% filter(PT_actual >= 0)

# add bins for PT analyses
ExperimentSix_forced = ExperimentSix_forced %>% mutate(PT_actual_bins = split_quantile(PT_actual,12)) # ok weirdly 12 bins of one and 10 of the other whoops
ExperimentSix_forced = ExperimentSix_forced %>% mutate(PT_planned_bins = split_quantile(PT_planned,10))
 



ExperimentSix_forced$combinedType = NA
ExperimentSix_forced$combinedType[ExperimentSix_forced$coupletSwitch_actual == 0&ExperimentSix_forced$handSwitch_actual == 0] = 'rep/rep/sw'
ExperimentSix_forced$combinedType[ExperimentSix_forced$coupletSwitch_actual == 0&ExperimentSix_forced$handSwitch_actual == 1] = 'sw/rep/sw'
ExperimentSix_forced$combinedType[ExperimentSix_forced$coupletSwitch_actual == 1&ExperimentSix_forced$handSwitch_actual == 0] = 'rep/sw/sw'
ExperimentSix_forced$combinedType[ExperimentSix_forced$coupletSwitch_actual == 1&ExperimentSix_forced$handSwitch_actual == 1] = 'sw/sw/sw'
ExperimentSix_forced$combinedType[ExperimentSix_forced$fingerSwitch_actual == 0] = 'rep/rep/rep'
ExperimentSix_forced$combinedType[ExperimentSix_forced$trialNum == 1] = NA

  ExperimentSix_forced$treeDistance = NA
ExperimentSix_forced$treeDistance[ExperimentSix_forced$coupletSwitch_actual == 0&ExperimentSix_forced$handSwitch_actual == 0] = 2
ExperimentSix_forced$treeDistance[ExperimentSix_forced$coupletSwitch_actual == 0&ExperimentSix_forced$handSwitch_actual == 1] = 6
ExperimentSix_forced$treeDistance[ExperimentSix_forced$coupletSwitch_actual == 1&ExperimentSix_forced$handSwitch_actual == 0] =4
ExperimentSix_forced$treeDistance[ExperimentSix_forced$coupletSwitch_actual == 1&ExperimentSix_forced$handSwitch_actual == 1] = 6
ExperimentSix_forced$treeDistance[ExperimentSix_forced$fingerSwitch_actual == 0] = 0
ExperimentSix_forced$treeDistance[ExperimentSix_forced$trialNum == 1] = NA

ExperimentSix_forced$corrresp_prev = NA
ExperimentSix_forced$corrresp_prev[2:length(ExperimentSix_forced$corrresp_prev)] = ExperimentSix_forced$corrresp[1:(length(ExperimentSix_forced$corrresp_prev)-1)]
featureSwitchArray = array(c(0,1,1,2,3,2,2,1, 
                             1,0,2,1,2,3,1,2,
                             1,2,0,1,2,1,3,2,
                             2,1,1,0,1,2,2,3,
                             3,2,2,1,0,1,1,2,
                             2,3,1,2,1,0,2,1,
                             2,1,3,2,1,2,0,1,
                             1,2,2,3,2,1,1,0),dim = c(8,8))
ExperimentSix_forced$nFeatureSwitch[1] = NA
for(ai in 1:length(ExperimentSix_forced$nFeatureSwitch)){
  prev = ExperimentSix_forced$corrresp_prev[ai]
  curr = ExperimentSix_forced$corrresp[ai]
  ExperimentSix_forced$nFeatureSwitch[ai] = featureSwitchArray[prev,curr]
}
ExperimentSix_forced$nFeatureSwitch[ExperimentSix_forced$trialNum == 1] = NA

# Add column for error type
ExperimentSix_forced$errorType = NA
ExperimentSix_forced$errorType[ExperimentSix_forced$corr == 1] = '1/1/1'
ExperimentSix_forced$errorType[ExperimentSix_forced$corr == 0 & ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 1] = '1/1/0'
ExperimentSix_forced$errorType[ExperimentSix_forced$corr == 0 & ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 0] = '1/0/0'
ExperimentSix_forced$errorType[ExperimentSix_forced$corr == 0 & ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 1] = '0/1/0'
ExperimentSix_forced$errorType[ExperimentSix_forced$corr == 0 & ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 0] = '0/0/0'

#set up corr finger column
ExperimentSix_forced$corrFinger = NA
ExperimentSix_forced$corrFinger[ExperimentSix_forced$corrresp %in% c(1,3,5,7) & ExperimentSix_forced$resp %in% c(1,3,5,7)] = 1
ExperimentSix_forced$corrFinger[ExperimentSix_forced$corrresp %in% c(2,4,6,8) & ExperimentSix_forced$resp %in% c(2,4,6,8)] = 1
ExperimentSix_forced$corrFinger[ExperimentSix_forced$corrresp %in% c(1,3,5,7) & ExperimentSix_forced$resp %in% c(2,4,6,8)] = 0
ExperimentSix_forced$corrFinger[ExperimentSix_forced$corrresp %in% c(2,4,6,8) & ExperimentSix_forced$resp %in% c(1,3,5,7)] = 0

ExperimentSix_forced$errorType2 = NA
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 1 & ExperimentSix_forced$corrFinger == 1] = '1/1/1'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 1 & ExperimentSix_forced$corrFinger == 0] = '1/1/0'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 0 & ExperimentSix_forced$corrFinger == 1] = '1/0/1'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 1 & ExperimentSix_forced$corrCouplet == 0 & ExperimentSix_forced$corrFinger == 0] = '1/0/0'

ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 1 & ExperimentSix_forced$corrFinger == 1] = '0/1/1'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 1 & ExperimentSix_forced$corrFinger == 0] = '0/1/0'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 0 & ExperimentSix_forced$corrFinger == 1] = '0/0/1'
ExperimentSix_forced$errorType2[ExperimentSix_forced$corrHand == 0 & ExperimentSix_forced$corrCouplet == 0 & ExperimentSix_forced$corrFinger == 0] = '0/0/0'


#convert what you need into factors to stop from droppipng in groups
ExperimentSix_forced$subject = as.factor(ExperimentSix_forced$subject)
ExperimentSix_forced$errorType = as.factor(ExperimentSix_forced$errorType)
ExperimentSix_forced$treeDistance = as.factor(ExperimentSix_forced$treeDistance)
ExperimentSix_forced$PT_actual_bins = as.factor(ExperimentSix_forced$PT_actual_bins)
ExperimentSix_forced$PT_planned_bins = as.factor(ExperimentSix_forced$PT_planned_bins)
ExperimentSix_forced$combinedType = as.factor(ExperimentSix_forced$combinedType)


# mark subjects that shoudl be inlcuded from the learnign sample
ExperimentSix_forced$includeLearn = NA
ExperimentSix_forced$includeLearn[ExperimentSix_forced$subject %in% subjNums_included] = 1

ExperimentSix_forced$timing_chill = NA
ExperimentSix_forced$timing_chill[abs(ExperimentSix_forced$rt)<=.25] = 1

# filter out PT_actual of over 1.75s
ExperimentSix_forced_withExclusions = ExperimentSix_forced %>% filter(PT_actual <= 1.75, includeLearn == 1)

# Add bins of time for analysis
# method one
ExperimentSix_forced_withExclusions$eml = NA
ExperimentSix_forced_withExclusions$eml[ExperimentSix_forced_withExclusions$PT_actual <= .4] = 'a_early'
ExperimentSix_forced_withExclusions$eml[ExperimentSix_forced_withExclusions$PT_actual > .4 & ExperimentSix_forced_withExclusions$PT_actual <= .8] = 'b_mid'
ExperimentSix_forced_withExclusions$eml[ExperimentSix_forced_withExclusions$PT_actual > .8] = 'c_late'
# method two
ExperimentSix_forced_withExclusions$eml2 = NA
ExperimentSix_forced_withExclusions$eml2[ExperimentSix_forced_withExclusions$PT_actual <= .5] = 'a_early'
ExperimentSix_forced_withExclusions$eml2[ExperimentSix_forced_withExclusions$PT_actual > .5 & ExperimentSix_forced_withExclusions$PT_actual <= .9] = 'b_mid'
ExperimentSix_forced_withExclusions$eml2[ExperimentSix_forced_withExclusions$PT_actual > .9] = 'c_late'
# method three
ExperimentSix_forced_withExclusions$eml3 = NA
ExperimentSix_forced_withExclusions$eml3[ExperimentSix_forced_withExclusions$PT_actual <= .3] = 'a_early1'
ExperimentSix_forced_withExclusions$eml3[ExperimentSix_forced_withExclusions$PT_actual > .5 & ExperimentSix_forced_withExclusions$PT_actual <= .7] = 'b_mid1'
ExperimentSix_forced_withExclusions$eml3[ExperimentSix_forced_withExclusions$PT_actual > .7 & ExperimentSix_forced_withExclusions$PT_actual <= .9] = 'b_mid2'
ExperimentSix_forced_withExclusions$eml3[ExperimentSix_forced_withExclusions$PT_actual > .9& ExperimentSix_forced_withExclusions$PT_actual <= 1.1] = 'c_late1'
ExperimentSix_forced_withExclusions$eml3[ExperimentSix_forced_withExclusions$PT_actual > 1.1] = 'c_late2'

ExperimentSix_forced_withExclusions$corrFinger = NA
ExperimentSix_forced_withExclusions$corrFinger[ExperimentSix_forced_withExclusions$corrresp %in% c(1,3,5,7) & ExperimentSix_forced_withExclusions$resp %in% c(1,3,5,7)] = 1
ExperimentSix_forced_withExclusions$corrFinger[ExperimentSix_forced_withExclusions$corrresp %in% c(2,4,6,8) & ExperimentSix_forced_withExclusions$resp %in% c(2,4,6,8)] = 1
ExperimentSix_forced_withExclusions$corrFinger[ExperimentSix_forced_withExclusions$corrresp %in% c(1,3,5,7) & ExperimentSix_forced_withExclusions$resp %in% c(2,4,6,8)] = 0
ExperimentSix_forced_withExclusions$corrFinger[ExperimentSix_forced_withExclusions$corrresp %in% c(2,4,6,8) & ExperimentSix_forced_withExclusions$resp %in% c(1,3,5,7)] = 0

ExperimentSix_forced_withExclusions$errorType2 = NA
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 1 & ExperimentSix_forced_withExclusions$corrCouplet == 1 & ExperimentSix_forced_withExclusions$corrFinger == 1] = '1/1/1'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 1 & ExperimentSix_forced_withExclusions$corrCouplet == 1 & ExperimentSix_forced_withExclusions$corrFinger == 0] = '1/1/0'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 1 & ExperimentSix_forced_withExclusions$corrCouplet == 0 & ExperimentSix_forced_withExclusions$corrFinger == 1] = '1/0/1'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 1 & ExperimentSix_forced_withExclusions$corrCouplet == 0 & ExperimentSix_forced_withExclusions$corrFinger == 0] = '1/0/0'

ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 0 & ExperimentSix_forced_withExclusions$corrCouplet == 1 & ExperimentSix_forced_withExclusions$corrFinger == 1] = '0/1/1'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 0 & ExperimentSix_forced_withExclusions$corrCouplet == 1 & ExperimentSix_forced_withExclusions$corrFinger == 0] = '0/1/0'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 0 & ExperimentSix_forced_withExclusions$corrCouplet == 0 & ExperimentSix_forced_withExclusions$corrFinger == 1] = '0/0/1'
ExperimentSix_forced_withExclusions$errorType2[ExperimentSix_forced_withExclusions$corrHand == 0 & ExperimentSix_forced_withExclusions$corrCouplet == 0 & ExperimentSix_forced_withExclusions$corrFinger == 0] = '0/0/0'

ExperimentSix_forced_withExclusions$errorType2 = as.factor(ExperimentSix_forced_withExclusions$errorType2)

######### WRITE DATA TO FILE ########
write.csv(ExperimentSix_forced_withExclusions, 'Experiment6_forced_compiled.csv')
```